---
title: "Establishing relationships between LWC and MPa, Part 2"
author: "Indra Boving"
date: "11/9022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(boot)
source(here::here("scripts", "scripts_functions", "figure_info.R"))
```

```{r}
data_og <- read_csv( here("processed-data", paste0("analysis",datver,".csv"))) %>% 
  select(tree, week, water_potential, lwc, time_season, time, date_wp) %>% 
  distinct()

unique(data_og$week)
```


#TIME:
```{r}
data_all <- data_og %>% 
  filter(time == "md") 

# Filter for trees measured "before leafout"
before_leafout_data <- data_all %>%
  filter(time_season == "before leafout")

# Filter for trees measured "after leafout"
after_leafout_data <- data_all %>%
  filter(time_season == "after leafout")

# Find the common set of trees that appear in both datasets
common_trees <- intersect(before_leafout_data$tree, after_leafout_data$tree)

# Filter the original dataset to include only the common trees
common_trees_data <- data_all %>%
  filter(tree %in% common_trees)

# Assuming you have the 'common_trees_data' dataframe

# Get the unique tree IDs in 'common_trees_data'
unique_tree_ids <- unique(common_trees_data$tree)

# Count the number of unique tree IDs
num_unique_tree_ids <- length(unique_tree_ids)

# Print the number of unique tree IDs
cat("Number of unique tree IDs in common_trees_data:", num_unique_tree_ids, "\n")

# Filter the original dataset to include only the common tree IDs
filtered_data <- data_all[data_all$tree %in% common_trees, ] 
```

Pull 40 trees, get mean slope for those 40, do 1000x. 


###Before leafout: 
```{r}
data <- filtered_data  %>% 
  filter(time_season == "before leafout") %>% 
  distinct() %>% 
  drop_na(water_potential, lwc) %>% 
  filter(!tree %in% c(2012, 2011))

num_unique_trees <- length(unique(data$tree))
cat("Number of unique trees in the dataset:", num_unique_trees, "\n")

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- 37  # Adjust as needed

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ lwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_before <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_before)

summary(tbootstrapped_slopes_df_before)

mean_slope_before = tbootstrapped_slopes_df_before %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "before leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_before
```

###After leafout: 
```{r}
data <- common_trees_data %>% 
  filter(time_season == "after leafout") %>% 
  select(tree, week, water_potential, lwc) %>% 
  distinct() %>% 
  drop_na(water_potential, lwc)

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- 37  # Adjust as needed

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ lwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_after <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_after)

summary(tbootstrapped_slopes_df_after)

mean_slope_after = tbootstrapped_slopes_df_after %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "after leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_after
```

```{r}
#Combining before and after: 
time_boot_df <- bind_rows(mean_slope_before, mean_slope_after) %>% 
  select(pre_post, mean_slope, lower_bound, upper_bound) %>% 
  distinct() %>% 
  mutate(analysis = "time, ind. tree")
```

```{r}
time_boot_df %>% 
  group_by(pre_post) %>% 
  mutate(tree_mean = mean(mean_slope, na.rm = T)) %>% 
  ggplot() +
  geom_point(aes(y = tree_mean, 
             x = pre_post)) +
  geom_point(aes(y = upper_bound, 
                 x= pre_post), color = "blue")  +
  geom_point(aes(y = lower_bound, 
                 x= pre_post), color = "pink")  +
  theme_minimal()
```

#SPACE: 

UPDATE: don't actually need to do all of this, using SE CIs instead. 

```{r}
data <- data_og %>% 
  filter(time == "md") %>% 
  select(tree, week, water_potential, lwc) %>% 
  distinct() %>% 
  drop_na(lwc, water_potential)

head(data)

data %>% 
ggplot(aes(y = water_potential, 
           x = lwc, 
           color = as.factor(week))) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", se = F)
```
Cant actually filter by trees that were in all weeks, because none were actually sampled in all weeks. Maybe just ignore? 

```{r}
# Define the number of bootstrap iterations
n_iterations <- 1000

# Create an empty dataframe to store results
final_df_space <- data.frame(week = integer(), mean_slope = numeric(), lower_bound = numeric(), upper_bound = numeric())

# Get unique weeks in your dataset
unique_weeks <- unique(data$week)

# Iterate through each week
for (x in unique_weeks) {
  # Step 1: Filter data for the current week
  week_data <- data %>%
    filter(week == x)
  
  # Step 2: Initialize a container to store bootstrapped slopes
  slopes <- vector("double", length = n_iterations)
  
  # Step 3: Perform bootstrapping to estimate slopes
  for (i in 1:n_iterations) {
    # Randomly sample rows with replacement
    boot_indices <- sample(nrow(week_data), replace = TRUE)
    boot_sample <- week_data[boot_indices, ]
    
    # Calculate the slope for the bootstrapped sample
    model <- lm(water_potential ~ lwc, data = boot_sample)
    slopes[i] <- coef(model)[2]
  }
  
  # Step 4: Calculate the mean slope and 95% CI
  mean_slope <- mean(slopes)
  lower_bound <- quantile(slopes, 0.025)
  upper_bound <- quantile(slopes, 0.975)
  
  # Step 5: Store the results in the final dataframe
  final_df_space <- bind_rows(final_df_space, data.frame(week = x, mean_slope = mean_slope, lower_bound = lower_bound, upper_bound = upper_bound))
}

# Print the final dataframe
print(final_df_space)
```


```{r}
final_df_space %>% 
  ggplot(aes(x = week)) +
   geom_segment(aes(y= lower_bound, 
                   yend = upper_bound, 
                   x = week, 
                   xend = week, 
                   color = as.factor(week)))+
  geom_point(aes(y = mean_slope), color = "cyan") +
  geom_point(aes(y = lower_bound), color = "pink") +
  geom_point(aes(y = upper_bound), color = "gold") +
  geom_hline(yintercept =0) +
  labs(y = "Slope",
       x = "Week")
  
```
#HYDRATION: 

```{r}
data <- data_og %>% 
  select(tree, week, water_potential, lwc, time) %>%
  drop_na(lwc, water_potential) %>% 
  group_by(tree, week) %>%
  filter(all(c("pd", "md") %in% time)) %>%
  ungroup() %>% 
  distinct() 

head(data)
unique(data$week)
```

```{r}
df_all_groups <- data %>% 
  mutate(tree_week = paste(tree, week, sep = "_")
  ) %>% 
  mutate(water_potential = water_potential)
  

df_grey <- df_all_groups

df_1 <- df_all_groups %>% 
  filter(week %in% c('10'))

df_2 <- df_all_groups %>% 
  filter(week %in% c('19'))

df_3 <- df_all_groups %>% 
  filter(week %in% c('21'))

df_4 <- df_all_groups %>% 
  filter(week %in% c('37'))

nice_hydration_layered <- ggplot() +
    geom_point(aes(y = water_potential, x = lwc, shape = time), data = df_grey, color = "grey") +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week), color = "grey", data = df_grey) +
    geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_1"), 
               data = df_1 ) +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_1"), 
              data = df_1) +
    geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_2"), 
               data = df_2) +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_2"), 
              data = df_2) +
    # geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_3"), 
    #            data = df_3) +
    # geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_3"), 
    #           data = df_3) +
    # geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_4"), 
    #            data = df_4) +
    # geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_4"), 
    #           data = df_4
    #           ) +
    scale_colour_manual(name = 'Week', 
         values =c("df_1" ="#122451", 
                   "df_2"="#62929a",
                  # "df_3"="#EC7E28",
                   "df_4"="#c969a8"
                   ), 
         labels = c('10',
                    '17',
                  #  '21',
                    '33')) +
    labs(y = "Water Potential (MPa)", 
       x = "Leaf Water Content (g)", 
       color= "Week", 
       shape = "Time"
       #caption = "triangles = predawn, circles = midday"
       ) +
  theme(
    #legend.position = c(.9, .35),
   # legend.position = "none",
     legend.position = "right",
  #strip.background = element_blank(),
  #strip.text.y = element_blank(), 
  #strip.text.x = element_text(size = 16), 
  axis.text.y = element_text(size = 12), 
  axis.text.x = element_text(size = 12), 
  #axis.ticks.y = element_blank(), 
  axis.title.y = element_text(size = 20), 
  axis.title.x = element_text(size = 20), 
 # axis.title.x = element_blank(),
  legend.title = element_text(size = 14), 
  legend.text = element_text(size = 14), 
# legend.position = "none"
  ) +
   xlim(.5,2) +
  scale_x_reverse()
nice_hydration_layered

data_og %>% 
  ggplot(aes(y = lwc, x = week)) +
  geom_point()+
  facet_wrap(~time)
```

```{r, warning = F}
data %>% 
  filter(week == '10') %>% 
  mutate(tree_week = paste(tree, week, sep = "_")
  ) %>% 
  mutate(water_potential = water_potential) %>% 
  ggplot(aes(y = water_potential, x = lwc, color =    as.factor(tree))) +
    geom_point(aes(shape = time)) +
  geom_smooth(method = "lm")

```

Pull 40 trees, get mean slope for those 40, do 1000x. 
```{r}
# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 100

# Number of random trees to sample
n_sample_trees <- 37  # Adjust as needed

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ lwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

# Iterate through each unique week
unique_weeks <- unique(data$week)

for (x in unique_weeks) {
  # Filter data for the current week
  week_data <- data %>%
    filter(week == x)

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(week_data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- week_data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i, 
            week = x
          ) 
        ) 
      }
  }

}

# round1 <- bootstrapped_slopes_df %>% 
#   filter(round == 1)
summary_df_hyd <- bootstrapped_slopes_df %>%
        filter(slope > -100, slope < 100) %>% # remove v ulikely slopes
        drop_na(slope) %>%
        group_by(week, round) %>% #get the mean of each round and week
       mutate(slope_round = mean(slope, na.rm = T)) %>% 
          ungroup() %>% 
        group_by(week) %>% 
          mutate(mean_slope = mean(slope_round, na.rm = T),
          lower_bound = quantile(slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(slope_round, 0.975, na.rm = TRUE),
          week = week) %>% 
  select(week, mean_slope, lower_bound, upper_bound) %>% 
  distinct()
```



```{r}
summary_df_hyd %>% 
  ggplot(aes(x = week)) +
   geom_segment(aes(y= lower_bound, 
                   yend = upper_bound, 
                   x = week, 
                   xend = week, 
                   color = as.factor(week)))+
  geom_point(aes(y = mean_slope), color = "cyan") +
  geom_point(aes(y = lower_bound), color = "pink") +
  geom_point(aes(y = upper_bound), color = "gold") +
  labs(y = "Slope",
       x = "Week")
```
#COMBINE

Should be week, mean_slope, lower_bound, upper_bound

```{r}
final_df_hyd <- summary_df_hyd %>% 
  mutate(analysis = "hydration, ind. trees", 
         time_season = "NA")

unique(final_df_hyd$week)
final_df_space <- final_df_space %>% 
  mutate(analysis = "space", 
         time_season = "NA")

time_boot_df <- time_boot_df %>% 
  mutate(week = 0,
         time_season = pre_post)

final_df_all <- bind_rows(final_df_hyd, final_df_hyd, final_df_space, final_df_time, time_boot_df) %>% 
  mutate(slope = mean_slope, 
         lwr = lower_bound, 
         upr = upper_bound) %>% write_csv(here::here("processed-data", "bootstrapped_df_lwc_qudo.csv"))
```

