---
title: "Establishing relationships between cwc and MPa, Part 2"
author: "Indra Boving"
date: "11/9022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(boot)
source(here::here("scripts", "scripts_functions", "figure_info.R"))

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

library(cowplot)
library(grid)
library(gridExtra)

#source(here::here("scripts", "scripts_functions", "figure_info.R"))

datver <- "20230724" #make sure this matches the datver in the processing script
dataversion <- paste0("Data_", datver)
```

#DATA

```{r}
data_og <- read_csv(here("processed-data", paste0("cwc_analysis",datver,".csv")), show_col_types = F) %>%  
  filter(species %in% c("blue oak")) %>% 
  select(tree, week, water_potential, cwc, time_season, time, site, date_wp) %>% 
  distinct() %>% 
   # filter(!tree %in% c(2012, 2011)) %>% 
  filter(!(tree %in% c(2346))) %>% #this tree seems to have a problem with post-leafout cwc - all 0s - likely becuase the canopy was too small to see. 
  filter(!week %in% 11) #week 11 only has 9 midday measurements and acts really odd (2022-03-15) 
```
#--------------

#Bootstrapping

##TIME:
```{r}
data_all <- data_og %>% 
  filter(time == "md") 

# Filter for trees measured "before leafout"
before_leafout_data <- data_all %>%
  filter(time_season == "before leafout")

# Filter for trees measured "after leafout"
after_leafout_data <- data_all %>%
  filter(time_season == "after leafout")

# Find the common set of trees that appear in both datasets
common_trees <- intersect(before_leafout_data$tree, after_leafout_data$tree)

# Filter the original dataset to include only the common trees
common_trees_data <- data_all %>%
  filter(tree %in% common_trees)

# Assuming you have the 'common_trees_data' dataframe

# Get the unique tree IDs in 'common_trees_data'
unique_tree_ids <- unique(common_trees_data$tree)

# Count the number of unique tree IDs
num_unique_tree_ids <- length(unique_tree_ids)

# Print the number of unique tree IDs
cat("Number of unique tree IDs in common_trees_data:", num_unique_tree_ids, "\n")

# Filter the original dataset to include only the common tree IDs
filtered_data <- data_all[data_all$tree %in% common_trees, ] 

plotly::ggplotly(filtered_data %>% 
  drop_na(week)  %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE, 
             label = tree)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2) +
  color_two_grey)
```

Pull 40 trees, get mean slope for those 40, do 1000x. 


###Before leafout: 
```{r}
data <- filtered_data  %>% 
  filter(time_season == "before leafout", 
         !(week == 9)) %>% 
  distinct() %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT)

num_unique_trees <- length(unique(data$tree))
cat("Number of unique trees in the dataset:", num_unique_trees, "\n")

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- 42  # Adjust as needed based on the number of unique trees

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ cwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_before <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_before)

summary(tbootstrapped_slopes_df_before)

mean_slope_before = tbootstrapped_slopes_df_before %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "before leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_before
```

###After leafout: 
```{r}
data <- common_trees_data %>% 
  filter(time_season == "after leafout") %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(tree) %>% 
  mutate(COUNT = n()) %>% 
  filter(!(COUNT == 1)) %>% 
  select(-COUNT) 

num_unique_trees <- length(unique(data$tree))
cat("Number of unique trees in the dataset:", num_unique_trees, "\n")

# Assuming your dataset is called 'data'
# Make sure 'data' is properly loaded before proceeding

# Define the number of bootstrap iterations
n_iterations <- 1000

# Number of random trees to sample
n_sample_trees <- 39  # Adjust as needed

# Create an empty data frame to store bootstrapped slopes
bootstrapped_slopes_df <- data.frame()

# Function to calculate the slope for a specific tree within each iteration
calculate_slope_for_tree <- function(tree_data) {
  model <- lm(water_potential ~ cwc, data = tree_data)
  return(coef(model)[2])  # Extract the slope coefficient
}

#Do the bootstrapping: 

 for (i in 1:n_iterations) {
   
# Randomly sample 'n_sample_trees' trees from your dataset
sampled_tree_ids <- sample(unique(data$tree), size = n_sample_trees, replace = TRUE)

# Iterate through each sampled tree and perform bootstrapping separately
      for (tree_id in sampled_tree_ids) {
        
        tree_data <- data %>%
          filter(tree == tree_id)
        
        # Initialize a container to store slopes for each iteration
        slopes <- vector("double", length = 1)
      
          # Calculate the slope for the bootstrapped sample
          slopes[] <- calculate_slope_for_tree(tree_data)
        
        # Store the bootstrapped slopes for this tree in the data frame
        bootstrapped_slopes_df <- bind_rows(
          bootstrapped_slopes_df,
          data.frame(
            tree = tree_id,
            slope = slopes, 
            round = i
          ) 
        ) 
      }
 }

        ci_values <- bootstrapped_slopes_df %>%
        group_by(round) %>% 
        drop_na(slope) %>%
       mutate(
          mean_slope_round = mean(slope, na.rm = T)
        ) %>% 
          ungroup() %>% 
          mutate(mean = mean(mean_slope_round, na.rm = T),
          lower_bound = quantile(mean_slope_round, 0.025, na.rm = TRUE),
          upper_bound = quantile(mean_slope_round, 0.975, na.rm = TRUE))
          
        
        # Merge the CI values back into the original dataframe
      tbootstrapped_slopes_df_after <- ci_values 
      
# Print the updated dataframe with CI values
print(tbootstrapped_slopes_df_after)

summary(tbootstrapped_slopes_df_after)

mean_slope_after = tbootstrapped_slopes_df_after %>% 
  mutate(mean_slope = mean(mean, na.rm = T),
         pre_post = "after leafout") %>% 
  select(mean_slope, lower_bound, upper_bound, pre_post) %>% 
  distinct()
mean_slope_after
```

```{r}
#Combining before and after: 
cwc_time_boot_df <- bind_rows(mean_slope_before, mean_slope_after) %>% 
  select(pre_post, mean_slope, lower_bound, upper_bound) %>% 
  distinct() %>% 
  mutate(analysis = "time, ind. tree")
```

```{r}
cwc_time_boot_df %>% 
  group_by(pre_post) %>% 
  mutate(tree_mean = mean(mean_slope, na.rm = T)) %>% 
  ggplot() +
  geom_point(aes(y = tree_mean, 
             x = pre_post)) +
  geom_point(aes(y = upper_bound, 
                 x= pre_post), color = "blue")  +
  geom_point(aes(y = lower_bound, 
                 x= pre_post), color = "pink")  +
  theme_minimal()
```

#SPACE: 

```{r}
data <- data_og %>% 
  filter(time == "md") %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(cwc, water_potential)

head(data)

data %>% 
ggplot(aes(y = water_potential, 
           x = cwc, 
           color = as.factor(week))) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", se = F)

#HOW MANY trees? 

data %>% 
  drop_na(water_potential, cwc) %>% 
  group_by(week) %>% 
  count()
```
Cant actually filter by trees that were in all weeks, because none were actually sampled in all weeks. Maybe just ignore? 

```{r}
# Define the number of bootstrap iterations
n_iterations <- 1000

# Create an empty dataframe to store results
cwc_final_df_space <- data.frame(week = integer(), mean_slope = numeric(), lower_bound = numeric(), upper_bound = numeric())

# Get unique weeks in your dataset
unique_weeks <- unique(data$week)

# Iterate through each week
for (x in unique_weeks) {
  # Step 1: Filter data for the current week
  week_data <- data %>%
    filter(week == x)
  
  # Step 2: Initialize a container to store bootstrapped slopes
  slopes <- vector("double", length = n_iterations)
  
  # Step 3: Perform bootstrapping to estimate slopes
  for (i in 1:n_iterations) {
    # Randomly sample rows with replacement
    boot_indices <- sample(nrow(week_data), replace = TRUE)
    boot_sample <- week_data[boot_indices, ]
    
    # Calculate the slope for the bootstrapped sample
    model <- lm(water_potential ~ cwc, data = boot_sample)
    slopes[i] <- coef(model)[2]
  }
  
  # Step 4: Calculate the mean slope and 95% CI
  mean_slope <- mean(slopes, na.rm = TRUE)
  lower_bound <- quantile(slopes, 0.025, na.rm = TRUE)
  upper_bound <- quantile(slopes, 0.975, na.rm = TRUE)
  
  # Step 5: Store the results in the final dataframe
  cwc_final_df_space <- bind_rows(cwc_final_df_space, 
                                  data.frame(week = x, 
                                             mean_slope = mean_slope,
                                             lower_bound = lower_bound, 
                                             upper_bound = upper_bound))
}

# Print the final dataframe
print(cwc_final_df_space)
```


```{r}
cwc_final_df_space %>% 
  ggplot(aes(x = week)) +
   geom_segment(aes(y= lower_bound, 
                   yend = upper_bound, 
                   x = week, 
                   xend = week, 
                   color = as.factor(week)))+
  geom_point(aes(y = mean_slope), color = "cyan") +
  geom_point(aes(y = lower_bound), color = "pink") +
  geom_point(aes(y = upper_bound), color = "gold") +
  geom_hline(yintercept =0) +
  labs(y = "Slope",
       x = "Week")
  
```

#COMBINE

Should be week, mean_slope, lower_bound, upper_bound

```{r}
cwc_final_df_space <- cwc_final_df_space %>% 
  mutate(analysis = "space", 
         time_season = "NA")

cwc_time_boot_df <- cwc_time_boot_df %>% 
  mutate(week = 0,
         time_season = pre_post)

final_df_all_cwc <- bind_rows(cwc_final_df_space, cwc_time_boot_df) %>% 
  mutate(slope = mean_slope, 
         lwr = lower_bound, 
         upr = upper_bound) 

final_df_all_cwc %>% write_csv(here::here("processed-data", "bootstrapped_df_cwc.csv"))
```

#------------

#Analysis: 

#Data wrangling: 

```{r, echo=F}
wc_qudo_df <- data_og %>% 
  drop_na(time)

wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)

wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  #drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(cwc, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(cwc_md, cwc_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
 # select(-date_wp) %>% 
  distinct()

wk_all_long_cwc <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = cwc_pd, 
         md = cwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "cwc") %>% 
  select(-cwc_pd, -cwc_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-cwc_md, -cwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_cwc) %>% 
  distinct() %>% 
 # select(-cwc_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(cwc = mean(cwc, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T), 
            site = site)
```


#SPACE:

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wk_all_long %>% 
  mutate(water_potential = water_potential) %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_cwc = mean(cwc, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(cwc_centered = cwc - mean_cwc)
  # mutate(cwc_centered = scale(cwc,  scale=FALSE)) %>% 
  # filter(cwc_centered < 4)
```


```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = cwc_centered, 
            x = cwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_text(size = 20), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice

ggsave(here("figures", "nice_space_cwc"), space_nice, device = "jpg", width = 6, height = 4, dpi = 300)
```

```{r, warning = F, echo=FALSE}
#scaled
space_nice_centered <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc_centered, 
            #x = cwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
        #legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 1))

space_nice_centered

ggsave(here("figures", "nice_space_centered"), space_nice_centered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Do we need to include site here? 

Centered cwc:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc_centered + (cwc_centered|week) + (1|tree), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ cwc_centered  + (cwc_centered|week) + (1|tree) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

NO

cwc uncentered:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc + (cwc|week) + (1|tree), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ cwc  + (cwc|week) + (1|tree) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
NO


Visualize: 

###Slopes, MD, Centered:

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ cwc_centered + (cwc_centered|week) + (1|tree), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc_centered`, 
         -cwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc_centered`)%>% 
  select(-`(Intercept)`, 
         -cwc_centered) %>% 
  tibble::rownames_to_column("week") %>% 
  mutate(week = as.numeric(week))

# weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
# weeks_check

# weeks <- data_frame(1:10)
# weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29, 33) 

ran_df_week_3 <- bind_cols(ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()

ran_df_week_3 %>% 
 # mutate(week = as.factor(week)) %>% 
  mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  color_grad +
   # color_many_2 +
  guides(color = guide_legend(nrow = 2))
```

Intercepts - centered

```{r, echo=FALSE}
ran_df_week_3 %>% 
   mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
    color_grad +
  guides(color = guide_legend(nrow = 2))
```

##Slopes, MD, NOT Centered

Get slopes from random effects: 

NOTE: this includes site random effect, which the centered version does not need. 

```{r, echo=FALSE}
space_mod_4 <- lmer(water_potential ~ cwc + (cwc|week) + (1|tree) + (1|site), data =  wc_wk_centered_df, REML = T)

space_mod_df_4 <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod_4)

#ran_list2 <- coef(m_wk_rand)

ran_df_4 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         -cwc) %>%
  select(-`(Intercept)`)

ran_err_4 <- arm::se.ranef(space_mod_4)

ran_err_df_4 <- as.data.frame(ran_err_4[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`)%>% 
  select(-`(Intercept)`, 
         -cwc) %>% 
  tibble::rownames_to_column("week")

ran_df_week_4 <- bind_cols(ran_df_4, ran_err_df_4) %>% 
  #select(-`1:10`) %>% 
  data_frame()

space_slope <- ran_df_week_4 %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slope
```
Intercept - not centered

```{r, echo=FALSE}
ran_df_week_4 %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```


###Slopes, from bootsrapping: 

```{r}
space_slopes <- final_df_all_cwc %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "space") %>% 
   mutate(week = as.factor(week)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slopes
```

#TIME

```{r}
wc_qudo_df %>% 
  drop_na(week) %>% 
  ggplot(aes(y = cwc, 
             x = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "cwc", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE, warning = F}
time <- wc_qudo_df %>% 
  drop_na(week) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2) +
  color_two_grey
time 

ggsave(here("figures", "nice_time"), time, device = "jpg", width = 4, height = 2, dpi = 300)
```



```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Predawn MPa") +
  #color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

All dates: 

Include site?

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree), data = space_df_nosite, REML = F)
#summary(space_mod)
AIC(space_mod)

space_mod_site <- lmer(water_potential ~ cwc  + (1|week) + (cwc|tree) + (1|site), data = space_df_nosite,  REML = F)

AIC(space_mod_site)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
YES
####All time



```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")

#with separate periods: 
time_season_mod <- lmer(water_potential ~ cwc + time_season + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)

time_season_mod_df <- broom::tidy(time_season_mod)

#with separate periods: 
time_season_mod_int <- lmer(water_potential ~ cwc*time_season + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)

time_season_mod_int_df <- broom::tidy(time_season_mod)

time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree)+ (1|site), data = wc_qudo_md_df)
#time_mod <- lmer(water_potential ~ cwc + (cwc|tree), data = wc_qudo_md_df)
 
MuMIn::r.squaredGLMM(time_mod)

summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = cwc
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
tree_eff

ran_err_tree1 <- arm::se.ranef(time_mod)

ran_err_tree2 <- as.data.frame(ran_err_tree1[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree <- bind_cols(tree_eff, ran_err_tree2) %>% 
  #select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))# +
  #color_very_many 

ran_df_tree %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = slope + (std.error), 
         lwr = slope - (std.error)) %>% 
  ggplot(aes(color= estimate)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = estimate))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none", 
        axis.text.x = element_blank())#+
  #theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

####Just linear: 
```{r}
lin_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "after leafout")
  
  
lin_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = lin_wc_qudo_md_df)
summary(lin_time_mod)

MuMIn::r.squaredGLMM(lin_time_mod)
```


```{r}
lin_ran_list <- coef(lin_time_mod)
lin_ran_list

lin_tree_eff <- as.data.frame(lin_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`,
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
lin_tree_eff

lin_ran_err_tree <- arm::se.ranef(lin_time_mod)

lin_ran_err_tree <- as.data.frame(lin_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

lin_ran_df_tree_after <- bind_cols(lin_tree_eff, lin_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame() %>% 
  mutate(time_season = "After Leafout")

#With standard errors around estimates:

#intercetps 
lin_ran_df_tree_after%>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Intercepts, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 


lin_ran_df_tree_after %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

lin_ran_df_tree_after %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```
####Before leafout: 

```{r}
bef_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "before leafout") %>% 
  drop_na(site)
  
  
bef_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = bef_wc_qudo_md_df, REML = T)
summary(bef_time_mod)


MuMIn::r.squaredGLMM(bef_time_mod)
```


```{r}
bef_ran_list <- coef(bef_time_mod)

bef_tree_eff <- as.data.frame(bef_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
bef_tree_eff

bef_ran_err_tree <- arm::se.ranef(bef_time_mod)

bef_ran_err_tree <- as.data.frame(bef_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
         -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

bef_ran_df_tree_before <- bind_cols(bef_tree_eff, bef_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()%>% 
  mutate(time_season = "Before Leafout")

bef_ran_df_tree_before %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, BEFORE LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) #+
 # color_very_many 

bef_ran_df_tree_before %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```

####Slopes, SE, pre- and post-

```{r}
ran_df_tree_before_vs_after <- bind_rows(bef_ran_df_tree_before, lin_ran_df_tree_after)

ef <- ran_df_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate(sd = sd(slope),
         slope = mean(slope), 
         mean_se = mean(std.error.slope),
        mean_std.error = mean(std.error),
        upr_sd = slope + mean_std.error,
        lwr_sd = slope - mean_std.error,
         upr = slope + mean_se,
         lwr = slope - mean_se,
         time_season = as.factor(time_season)) 
# %>% 
#   select(slope, upr, lwr, time_season, sd)

time_summary <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SE acrss all trees
            for each time frame", 
       x = "Time")
time_summary

time_summary_sd <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr_sd, x = time_season), size = 1) +
  geom_point(aes(y = lwr_sd, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr_sd, 
                   yend = upr_sd, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
            for each time frame", 
       x = "Time")
time_summary_sd

ggsave(here("figures", "time_summary_slopes"), time_summary, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

##Slopes, bootstrapping - inds
 
```{r}
time_summary_bs_tree <- final_df_all_cwc %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "time, ind. tree") %>% 
   mutate(week = as.factor(week)) %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Bootstrapped slope and CI", 
       x = "Time")
time_summary_bs_tree


ggsave(here("figures", "time_summary_slopes_boot_tree"), time_summary_bs_tree, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

#Models

```{r}
glance_df <- bind_rows(space_glance <- broom.mixed::glance(space_mod) 
                       %>% mutate(mod = "space"),
                       time_glance <- broom.mixed::glance(time_season_mod)
                       %>% mutate(mod = "time"),
                       time_glance <- broom.mixed::glance(time_season_mod_int)
                       %>% mutate(mod = "interaction"),
                       as_data_frame(r.squaredGLMM(space_mod)) 
                       %>% mutate(mod = "space"),
                       as_data_frame(r.squaredGLMM(time_season_mod)) 
                       %>% mutate(mod = "time"),
                       as_data_frame(r.squaredGLMM(time_season_mod_int)) 
                       %>% mutate(mod = "interaction")) %>% 
  group_by(mod) %>% 
  fill(c(R2m, R2c), .direction = "downup") %>% 
  distinct() %>% 
  drop_na(df.residual)
glance_df
```


```{r}
cwc_mods <- bind_rows(space_mod_df <- space_mod_df %>% mutate(mod = "space"),
                      time_season_mod_df <- time_season_mod_df %>% mutate(mod= "time"),
  time_season_mod_df <- time_season_mod_int_df %>% mutate(mod= "interaction")) %>% 
  bind_rows(glance_df) %>% 
  mutate(var = "cwc")

cwc_mods


write_csv(cwc_mods, here::here("processed-data", "cwc_mods.csv"))
```

#----------
#FIGURES

#####Space - faceted

```{r}
#scaled
space_nice_2 <- data_og %>% 
  filter(time == "md", 
         week %in% c(14, 19, 20, 37)) %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(cwc, water_potential) %>% 
  ggplot(aes(y = water_potential, 
            x = cwc,
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
    # legend.key=element_blank(), 
    #  axis.title.x = element_blank(),
   #  axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F,size = .5) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(#y= "Middays (MPa)", 
       y = "Middays (MPa)",
       x = "CWC (g/cm2)", 
       color = "Week", 
       shape = "Site") +
  #color_many_2 +
  color_week_assigned +
  guides(color = guide_legend(nrow = 1)) +
  facet_wrap(~week, nrow = 1)+
  #scale_x_reverse() +
scale_y_continuous(labels = scales::number_format(accuracy = 0.1))
space_nice_2

```

#Slopes: 

####Space

```{r}
space_slope <-  final_df_all_cwc%>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "space") %>% 
 # mutate(week = as.numeric(week)) %>% 
   ggplot(aes(color= as.factor(week))
    ) + 
  geom_point(aes(y = slope ,x = as.factor(week)), size =2) +
    geom_point(aes(y = upr, x = as.factor(week)), size = 1) +
  geom_point(aes(y = lwr, x = as.factor(week)), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = as.factor(week), 
                   xend = as.factor(week), 
                   color = as.factor(week)))+
  labs(x = "Week", 
       color = "Week", 
       y = " ") +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  #scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                  #   breaks = c(37, 33, 29, 21, 19, 17, 15, 14, 12, 10)
                      # seq(10, 30, by = 1)
  #                   ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  color_week_assigned +
 # color_many_2 +
  guides(color = guide_legend(nrow = 2))
 # scale_x_reverse()
space_slope

```


SE: 

```{r, eval = F}
# space_slope <- ran_df_week_4 %>% 
#   mutate(week = as.numeric(week)) %>% 
#  # filter(week %in% c(14, 17, 21, 29)) %>% 
#  # filter(term == "cwc") %>% 
#   mutate(upr = slope + (std.error.slope), 
#          lwr = slope - (std.error.slope)) %>% 
#   ggplot(aes(color= week)
#     ) + 
#   geom_point(aes(y = slope ,x = week), size =2) +
#     geom_point(aes(y = upr, x = week), size = 1) +
#   geom_point(aes(y = lwr, x = week), size = 1) +
#   #geom_line(aes(group = week, y = week, x = upr)) +
#   geom_segment(aes(y= lwr, 
#                    yend = upr, 
#                    x = week, 
#                    xend = week, 
#                    color = week))+
#   labs(x = "Week", 
#        color = "Week", 
#        y = " ") +
#   theme(legend.position="none",
#       strip.background = element_blank(),
#       strip.text.x = element_text(size = 12),
#       plot.title = element_text(size=13),
#       axis.title.y = element_text(size = 15),
#       axis.title.x = element_blank(),
#      axis.text = element_text(size = 12),
#      legend.key=element_blank(), 
#      legend.text = element_text(size = 13), 
#     # legend.title = element_text(size = 16),
#     legend.title = element_blank(),
#      legend.margin=margin(0,0,0,0),
#       legend.box.margin=margin(-5,-8,-8,-8)
#     ) +
#   scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
#                   #   breaks = c(37, 33, 29, 21, 19, 17, 15, 14, 12, 10)
#                       # seq(10, 30, by = 1)
#                      ) +
#   geom_hline(yintercept = 0, linetype="dotted") + 
#   color_grad_new +
#  # color_many_2 +
#   guides(color = guide_legend(nrow = 2)) 
# space_slope
```
####Time

BS:

```{r}
time_summary <- final_df_all_cwc%>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "time, ind. tree") %>% 
   mutate(week = as.factor(week), 
          time_season = case_when(
            time_season %in% c("before leafout") ~ "During", 
             time_season %in% c("after leafout") ~ "After", 
            
          )) %>% 
ggplot(aes(color = time_season)) + 
  geom_point(aes(y = slope, x = time_season), size =3) +
  geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "",
       x = "Time") +
  color_two_grey +
  geom_hline(yintercept = 0, linetype="dotted") + 
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  scale_x_discrete(limit = rev)
  
time_summary
```





#*FIGURES*


#Scatterplots:

#####Space

```{r}
#scaled
space_nice_1 <- data_og %>% 
  filter(time == "md") %>% 
  select(tree, week, water_potential, cwc) %>% 
  distinct() %>% 
  drop_na(cwc, water_potential) %>% 
  ggplot(aes(y = water_potential, 
            x = cwc,
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text.y = element_text(size = 12),
     axis.text.x = element_text(size = 12),
    # axis.text.x  = element_blank(),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
    plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  geom_smooth(method = "lm", se = F,size = .5) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(#y= "Middays (MPa)", 
       y = " ",
       x = "Leaf Water per Area", 
       color = "Week", 
       shape = "Site") +
  #color_many_2 +
  color_week_assigned +
 # xlim(.5,2) +
 # ylim(-5,0)+
  guides(color = guide_legend(nrow = 2)) +
  #scale_x_reverse() +
scale_y_continuous(labels = scales::number_format(accuracy = 0.1))
space_nice_1


```
#####Time:

```{r}
time_1 <- data_og %>% 
  mutate(time = case_when(
    time == "md" ~ "Midday", 
    time == "pd" ~ "Predawn"
  )) %>% 
  filter(time == "Midday") %>% 
  drop_na(week) %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .1)+
  geom_smooth(method = "lm", se = F, size = .5, alpha = .4) +
 # theme(legend.position = "none") +
  labs(x = "lwc_mean", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text.x = element_text(size = 12),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      #axis.title = element_text(size = 15),
     axis.title = element_blank(),
     axis.text = element_text(size = 12),
     axis.text.x = element_text(size = 12),
     legend.key=element_blank(),
     legend.text = element_text(size = 13),
     legend.title = element_text(size = 16),
     #legend.title = element_blank(),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8),
     plot.margin = unit(c(5.5, 5.5, 0, 5.5), units = "pt")
    ) +
  labs(#y= "Water Potential (MPa)", 
       y = "Water Potential (MPa)",
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  color_two_grey +
scale_y_continuous(labels = scales::number_format(accuracy = 0.1))

time_1 
```

######Legend:

```{r}
legend_plot <- data_og %>% 
  mutate(time = case_when(
    time == "md" ~ "Midday", 
    time == "pd" ~ "Predawn"
  )) %>% 
  filter(time == "Midday") %>% 
  filter(!(week == 9)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = water_potential,
             x = cwc,
             color = as.factor(week), 
            # shape = as.factor(time),
             )) +
  geom_point() +
  theme(legend.position="top",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
    legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F, size = .5) + 
  labs(color = "Week", 
       shape = "Time") +
  color_week_assigned +
 # ylim(0,2) +
  guides(color = guide_legend(nrow = 2))
legend_plot

legend_scatterplots <- cowplot::get_legend(legend_plot)
legend_scatterplots
```

#COMBINE

```{r}
library(grid)
#labels of slopes: 
y.grob1 <- textGrob("Slope", 
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15), rot=90)

x.grob1 <- textGrob("Time", 
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15))

combined_slopes_wide <- cowplot::plot_grid(space_slope, NULL, time_summary,
                                           # NULL, pv_slope,
                                   nrow = 1, 
                                  rel_widths = c(1, -.005, 1  #, -.02, .5
                                                 ), 
                                  labels = c("B", "", "D"#,"", "G"
                                             ),
                                  label_x = .1,
                                  #hjust= c(3, 0, 3),
                                  label_y = .98
                                  # rel_heights = c(.15, 1, .3), 
                                   #rel_widths = c(1, 1, 1), 
                                  # rel_widths = c(.7, .8, .7, .3)
                                   ) 

combined_slopes_wide

combined_slopes_wide_labels <- grid.arrange(arrangeGrob(combined_slopes_wide, 
                            left = y.grob1, 
                            bottom = x.grob1),
                            heights = c(1, .05))

#labels of scatterplots: 
y.grob2 <- textGrob("Water Potential (MPa)", 
                   gp=gpar(fontface="bold", #col="blue", 
                           fontsize=15), rot=90)

x.grob2 <- textGrob("Canopy Water Content (g/cm2)", 
                   gp=gpar(fontface="bold", #col="blue",
                           fontsize=15))


combined_plots_wide_nolegend <- cowplot::plot_grid(space_nice_1, NULL, 
                                      time_1,
                                   labels=c("A","", "C"),
                                   label_x = .1,
                                   label_y = .98,
                                   nrow = 1,
                                   rel_widths = c(1, -0, 1)
                                   #rel_widths = c(1, 1, 1)
                                   ) 
combined_plots_wide_nolegend

combined_plots_wide <- cowplot::plot_grid(legend_scatterplots,
                                      combined_plots_wide_nolegend,
                                          nrow = 2, 
                                          rel_heights = c(.2, 1))

combined_plots_wide_labels <- grid.arrange(arrangeGrob(combined_plots_wide, 
                                left = y.grob2, 
                                bottom = x.grob2,
                                heights = c(1, 0)))

combined_plots_all <- cowplot::plot_grid(
  combined_plots_wide_labels, 
  combined_slopes_wide_labels, 
          nrow = 2, 
          rel_heights = c(.75, .6))

combined_plots_all

ggsave(here("figures", "qudo figures", "CWC", "combined_plots_all_qudo"), combined_plots_all, device = "jpg", width = 8, height = 7, dpi = 300)
```
