---
title: "Data for Sloane & Naomi"
author: "Indra Boving"
date: "2023-12-20"
output: html_document
---
Goal: 

Species average + variance for sampling dates with most focal trees for '22 and '23  - hold out Pine Needle (because has deep water access)
- Psi_pd, Psi_md
-branch Al:As
-LMA
+ Phenology data (whatever we've got) from blues and ??? lives?

#Setup: 
```{r setup, include=FALSE}
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(plotrix)

datver <- 20231128
```

## Physiology Data: 

####2022

Creating a df that has mean, sd, and se of the following variable for each week that they were collected: 

Psi pd and Psi md 
Al:As
LMA

```{r}
sn_df_raw <- read_csv(here("processed-data", paste0("analysis_bothspp",datver,".csv")),show_col_types = FALSE) %>% 
  filter(is.na(date_wp))

sn_df_all <- read_csv(here("processed-data", paste0("analysis_bothspp",datver,".csv")),show_col_types = FALSE) %>% 
  select(date_wp, time, tree, plot, site, species, water_potential, lma_g_cm2, alas_cm2_per_mm2) %>% 
  filter(!(site == "PineNeedle")) %>% 
  mutate(date = case_when(
    date_wp %in% c("2022-04-06") ~ "2022-04-04",
    date_wp %in% c("2022-04-11") ~ "2022-04-13",
    date_wp %in% c("2022-03-03") ~ "2022-02-28",
    TRUE ~ as.character(date_wp)
  ), 
  date = ymd(date)) %>% 
  select(-date_wp) %>% 
  mutate(year = "2022", 
         water_potential = -1*water_potential)

#water potential summaries: 
sn_wp_df <- sn_df_all %>% 
   mutate(species = as.factor(species)) %>% 
  group_by(date, time, species) %>% 
  mutate(wp_mean = mean(water_potential, na.rm = T),
         wp_se = std.error(water_potential, na.rm = T), 
         wp_sd = sd(water_potential, na.rm = T)
         ) %>% 
  ungroup() %>% 
  select(date, species, time,
         wp_mean, wp_se, wp_sd)

#alas and lma summaries
sn_morph_df <- sn_df_all %>% 
  group_by(date, species) %>% 
    mutate(lma_mean = mean(lma_g_cm2, na.rm = T),
         lma_se = std.error(lma_g_cm2, na.rm = T), 
         lma_sd = sd(lma_g_cm2, na.rm = T),
         alas_mean = mean(alas_cm2_per_mm2, na.rm = T),
         alas_se = std.error(alas_cm2_per_mm2, na.rm = T), 
         alas_sd = sd(alas_cm2_per_mm2, na.rm = T)
         ) %>% 
  ungroup() %>% 
  select(date, species, 
         lma_mean, lma_sd, lma_se, 
         alas_mean, alas_sd, alas_se)

#put together in big df: 
sn_summaries_df <- merge(sn_wp_df, sn_morph_df, by = c("date", "species"), all = T) %>% 
  distinct() %>% 
  mutate(year = "2022", 
         date = ymd(date)) %>% 
  drop_na(date)
```

####2023

Psi pd and Psi md 
Al:As
LMA

```{r}
sn_wp_23_df1 <- read_csv(here::here("processed-data", "2023_wp.csv"),show_col_types = FALSE) %>% 
  mutate(time = pd_md, 
         tree = tag, 
         water_potential = water_potential_mpa,
         species = as.factor(species)) %>% 
  select(date, time, tree, plot, site, species, water_potential) %>% 
  filter(!(site == "PineNeedle")) 

sn_wp_23_df <- sn_wp_23_df1 %>% 
  mutate(species = as.factor(species)) %>% 
  group_by(date, time, species) %>% 
  mutate(wp_mean = mean(water_potential, na.rm = T),
         wp_se = std.error(water_potential, na.rm = T), 
         wp_sd = sd(water_potential, na.rm = T)
         ) %>% 
  ungroup() %>% 
  select(date, species, time,
         wp_mean, wp_se, wp_sd) %>% 
  distinct()

sn_morph_23_df1 <- read_csv(here::here("processed-data", "2023_alas.csv"),show_col_types = FALSE)  %>% 
  select(date, tree, plot, site, species, lma_g_cm2, alas_cm2_per_mm2) %>% 
  distinct() %>% 
  filter(!(site == "PineNeedle")) 

sn_morph_23_df <- sn_morph_23_df1 %>%  
  mutate(species = as.factor(species)) %>% 
  group_by(date, species) %>% 
    mutate(lma_mean = mean(lma_g_cm2, na.rm = T),
         lma_se = std.error(lma_g_cm2, na.rm = T), 
         lma_sd = sd(lma_g_cm2, na.rm = T),
         alas_mean = mean(alas_cm2_per_mm2, na.rm = T),
         alas_se = std.error(alas_cm2_per_mm2, na.rm = T), 
         alas_sd = sd(alas_cm2_per_mm2, na.rm = T)
         ) %>% 
  ungroup() %>% 
  select(date, species,
         lma_mean, lma_sd, lma_se, 
         alas_mean, alas_sd, alas_se) %>% 
  distinct()

sn_23_df <- merge(sn_wp_23_df1, sn_morph_23_df1, by = c("date", "species", "site", "plot", "tree"), all = T) %>% 
  mutate(year = "2023") %>% 
  group_by(tree, time, date) %>% 
  mutate(water_potential = mean(water_potential, na.rm= T),
         alas_cm2_per_mm2 = mean(alas_cm2_per_mm2, na.rm = T), 
         lma_g_cm2 = mean(lma_g_cm2, na.rm = T)) %>% 
  ungroup() %>% 
  distinct()

sn_summaries_23_df <- merge(sn_wp_23_df, sn_morph_23_df, by = c("date", "species"), all = T) %>% 
  distinct() %>% 
  mutate(year = "2023") %>% 
  filter(species %in% c("blue oak", "live oak"))
```

#COMBINE '22 and '23: 

```{r}
sn_summaries_all_df <- bind_rows(sn_summaries_23_df, sn_summaries_df) #%>% 
 # pivot_wider(names_from = "time",
 #    values_from = c(4:6),
 #   values_fn = mean) %>%
 # distinct()

sn_all_df <- bind_rows(sn_23_df, sn_df_all) %>% 
  drop_na(time) #%>% 
  # pivot_wider(names_from = "time", 
  #             values_from = "water_potential", 
  #             values_fn = mean) %>% 
  # rename(pd_mpa = pd, 
  #        md_mpa = md)

write_csv(sn_summaries_all_df, here::here("processed-data", "wp_morph_summaries_22_23.csv"))

write_csv(sn_all_df, here::here("processed-data", "wp_morph_alldates_22_23.csv"))

sn_all_df %>% 
  ggplot(aes(y = water_potential, 
             x = alas_cm2_per_mm2)) +
  geom_point() +
  facet_wrap(~year*time)

sn_all_df %>% 
  ggplot(aes(x = date, 
             y = alas_cm2_per_mm2, 
             color = species)) +
  geom_point() +
  facet_wrap(~year*time)
```

#Phenology: 

```{r}
pheno_sn_22_df <- read_csv(here("processed-data", paste0("phenology20230724.csv"))) %>% 
  mutate(year = "2022") %>% 
  select(2:5)

pheno_23_df <- read_csv(here(paste0("Data_",datver), "phenology.csv"),
                     show_col_types = FALSE) %>% 
  janitor::clean_names() %>% 
  mutate(tree = tree_id, 
         date = mdy(date), 
         pheno_score = phenology_score_0_10_new, 
         year = "2023"
         ) %>% 
  select(tree, date, pheno_score, year)

sn_pheno_all <- bind_rows(pheno_23_df, pheno_sn_22_df) %>% 
  merge(read_csv(here("processed-data", "trees_sites.csv")), by = c("tree"))

sn_pheno_all %>% 
  ggplot(aes(y = pheno_score, 
             x = date, 
             color = species))+
  geom_point() +
  facet_wrap(~year, scales = "free")

write_csv(sn_pheno_all, here("processed-data", "pheno_22_23.csv"))
```

