---
title: "Establishing relationships between lwc_mean and MPa, Part 2"
author: "Indra Boving"
date: "11/9022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#install.packages("")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

source(here::here("scripts", "scripts_functions", "figure_info.R"))

#datver <- "20230724"
dataversion <- paste0("Data_", datver)
```

#Data wrangling: 

```{r, echo=F}
wc_all_raw <- read_csv(here("processed-data", paste0("analysis",datver,".csv")), show_col_types = FALSE) 

wc_qudo_df <- wc_all_raw

wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)
```

What is the linear portion? 

```{r}
wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  ggplot(aes(y = alas_cm2_per_mm2, 
             x = date_wp, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  labs(title = "Alas")

wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  #filter(lma_g_cm2 < 0.05) %>% 
  ggplot(aes(y = water_potential, 
             x = date_wp, 
             color = as.factor(week)
             )) +
  geom_jitter() 
```

From what weeks do we have the most trees?
```{r, echo=F}
wc_qudo_df %>% 
  select(week, time, tree, lwc_mean) %>% 
  drop_na(lwc_mean) %>% 
  unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") + 
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "lwc_mean counts") +
  color_fill

wc_qudo_df %>% 
    select(week, time, tree, water_potential) %>% 
  drop_na(water_potential) %>% 
 # unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") +
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "MPa counts") +
  color_fill
```
A: week 17, 21, 29, 10

#Timeline

```{r, fig.height=.75, fig.width=6}
wc_qudo_df %>% 
  filter(time == "md") %>% 
  drop_na(water_potential) %>% 
  #ggplot(aes(x = week, y = 0, color = mean(water_potential, na.rm = T)))+
  ggplot(aes(x = week, y = 0, color = water_potential))+
  geom_hline(yintercept = 0) +
  geom_point(size = 5) +
  geom_point(data= wc_qudo_df %>% 
               filter(week %in% c(10, 12, 14,15, 17, 18, 19, 21, 37)), 
           pch=21, 
           size=5, 
           colour="black") +
  color_grad_rev +
  ylim(-.25, +.25)  + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 16,17, 18, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        )
```

```{r, fig.height=5, fig.width=6}
wc_qudo_df %>% 
  drop_na(water_potential) %>% 
  ggplot(aes(x = week, y = 0, color = water_potential))+
  geom_hline(yintercept = 0) +
  geom_point(size = 5) +
  facet_wrap(~time) + 
  color_grad_rev +
  labs(color = "Water Potential 
       (MPa)")+
  theme(legend.position = "right", 
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
       legend.title.align = -.5,
       legend.direction = "vertical",
       legend.key.size = unit(1, "cm")
        )

timeline_df <- wc_qudo_df %>% 
 # select(week, date_wp, time) %>% 
  mutate(date_wp = as.character(date_wp)) %>% 
  mutate(date_new = case_when(
    date_wp %in% c("2022-03-23") ~ "2022-03-25",
    date_wp %in% c("2022-03-30","2022-04-06") ~ "2022-04-04",
    date_wp %in% c("2022-04-13") ~ "2022-04-11",
    date_wp %in% c("2022-04-27") ~ "2022-04-25",
    date_wp %in% c("2022-05-04") ~ "2022-05-09",
    date_wp %in% c("2022-05-23") ~ "2022-05-25",
    TRUE ~ as.character(date_wp)
  )) %>% 
  mutate(date_new = ymd(date_new)) %>% 
  select(date_new, week, water_potential, time) %>% 
  distinct()


timeline_plot <- timeline_df %>% 
  drop_na(water_potential) %>% 
  filter(time == "md") %>% 
  ggplot(aes(x = date_new, 
             y = 0, 
             color = water_potential))+
  geom_hline(yintercept = 0) +
  geom_point(size = 10) +
    geom_point(data= timeline_df %>% 
               filter(week %in% c(10, 12, 14,15, 17, 18, 19, 21, 37)), 
           pch=21, 
           size=10, 
           stroke=2,
           colour="black") +
  color_grad_rev+
  ylim(-.25, +.25)  + 
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=.5, size= 20)
        ) +
scale_x_date(date_labels = '%b. %d',
             breaks = as.Date(c("2022-03-08","2022-03-15", "2022-03-25", 
                                #"2022-03-23", "2022-03-30", 
                                "2022-04-04", #"2022-04-06","2022-04-13", 
                                "2022-04-11", #"2022-04-27", 
                                "2022-04-25", #"2022-05-04" ,
                                "2022-05-09", "2022-05-25", 
                                #"2022-05-23", 
                                "2022-07-19", "2022-08-18","2022-09-15")))
timeline_plot

ggsave(here("figures", "timeline_plot"), timeline_plot, device = "jpg", width = 12, height = 2, dpi = 300)
```

#Phenology timelines
```{r, fig.height=2, fig.width=6}
fig_df <- wc_qudo_df %>% 
  group_by(week_alas_link, species) %>% 
  mutate(lma_all = lma_g_cm2,
        lma_g_cm2 = mean(lma_g_cm2, na.rm = T)) %>% 
  #filter(lma_g_cm2 < 0.08) %>% 
  select(week, species, lma_g_cm2) %>% 
  distinct() %>% 
  drop_na(lma_g_cm2) 


lma_plot <- fig_df %>%
  filter(week %in% c(10, 11, 13, 14, 17, 21, 29, 37, 40)) %>% ggplot(aes(x = week_alas_link, 
             y = lma_g_cm2)) +
  geom_point(size = 3) +
  geom_line() +
  scale_x_continuous(breaks = c(10, 11, 13, 14, 17, 21, 29, 37, 40)) +
  labs(y = "LMA") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 20), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        axis.text.x = element_text(hjust=.5, size= 20))
lma_plot

ggsave(here("figures", "lma_long_plot"), lma_plot, device = "jpg", width = 12, height = 2, dpi = 300)


fig_df <- wc_qudo_df %>% 
  group_by(week_alas_link, species) %>% 
  mutate(alas_cm2_per_mm2 = mean(alas_cm2_per_mm2, na.rm = T)) %>% 
  select(week, species, alas_cm2_per_mm2) %>% 
  distinct() %>% 
  drop_na(alas_cm2_per_mm2)

unique(fig_df$week)

alas_plot <- fig_df %>% 
  filter(week %in% c(c(10, 11, 13, 14, 17, 21, 29, 37, 40))) %>% 
  ggplot(aes(x = week_alas_link, 
             y = alas_cm2_per_mm2))+
  #geom_hline(yintercept = 0) +
  geom_point(size = 3) +
  geom_line() +
  scale_x_continuous(breaks = c(10, 11, 13, 14, 17, 21, 29, 37, 40)) +
  labs(y = "Al:As") +
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 20), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        axis.text.x = element_text(hjust=.5, size= 20)
        )
alas_plot

ggsave(here("figures", "alas_long_plot"), alas_plot, device = "jpg", width = 12, height = 2, dpi = 300)
```

#Bootsrapped dataset: 

Run: 
here::here("scripts", "3.2_bootstrapping.Rmd")
```{r}
final_df_all <- read_csv(here::here("processed-data", "bootstrapped_df_lwc.csv"))
```

#HYDRATION

MPa ~ lwc_mean + (lwc_mean|tree) + (1|wk)

```{r, warning = F}
wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(lwc_mean, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(lwc_mean_md, lwc_mean_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk_all_long_lwc_mean <- wk_all_wide %>% 
  drop_na(lwc_mean_pd, lwc_mean_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = lwc_mean_pd, 
         md = lwc_mean_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "lwc_mean") %>% 
  select(-lwc_mean_pd, -lwc_mean_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(lwc_mean_pd, lwc_mean_md, water_potential_md, water_potential_pd) %>% 
  select(-lwc_mean_md, -lwc_mean_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_lwc_mean) %>% 
  distinct() %>% 
 # select(-lwc_mean_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(lwc_mean = mean(lwc_mean, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T), 
            site = site)
```

#####Layered

```{r, echo=FALSE, fig.height= 5, fig.width= 10}
wk_figs <- wk_all_long %>% 
  filter(week %in% c(10, 14, 17, 19, 21, 29, 33, 37), 
         #lwc_mean < 6, 
        # lwc_mean > 0
         ) %>% 
  mutate(week_nice = case_when(
    week == 10 ~ "Week 10", 
    week == 14 ~ "Week 14", 
    week == 17 ~ "Week 17", 
    week == 19 ~ "Week 19", 
    week == 21 ~ "Week 21", 
    week == 29 ~ "Week 29",
    week == 33 ~ "Week 33",
    week == 37 ~ "Week 37"
  )) 

wk_figs_labels <-
  data.frame(
    label = c('10', '11', '17', '19', '21', '29', '33', '33'),
    week_nice = c(
      "Week 10",
      "Week 14",
      "Week 17",
      "Week 19",
      "Week 21",
      "Week 29",
      "Week 33",
      "Week 37"
    )
  )

df_all_groups <- wk_figs %>% 
  mutate(tree_week = paste(tree, week, sep = "_")
  ) %>% 
  mutate(water_potential = water_potential)
  

df_grey <- df_all_groups

df_1 <- df_all_groups %>% 
  filter(week %in% c('10'))

df_2 <- df_all_groups %>% 
  filter(week %in% c('17'))

df_3 <- df_all_groups %>% 
  filter(week %in% c('21'))

df_4 <- df_all_groups %>% 
  filter(week %in% c('37'))

nice_hydration_layered <- ggplot() +
    geom_point(aes(y = water_potential, x = lwc_mean, shape = time), data = df_grey, color = "grey") +
    geom_line(aes(y = water_potential, x = lwc_mean, group = tree_week), color = "grey", data = df_grey) +
    geom_point(aes(y = water_potential, x = lwc_mean, shape = time, color = "df_1"), 
               data = df_1 ) +
    geom_line(aes(y = water_potential, x = lwc_mean, group = tree_week, color = "df_1"), 
              data = df_1) +
    geom_point(aes(y = water_potential, x = lwc_mean, shape = time, color = "df_2"), 
               data = df_2) +
    geom_line(aes(y = water_potential, x = lwc_mean, group = tree_week, color = "df_2"), 
              data = df_2) +
    # geom_point(aes(y = water_potential, x = lwc_mean, shape = time, color = "df_3"), 
    #            data = df_3) +
    # geom_line(aes(y = water_potential, x = lwc_mean, group = tree_week, color = "df_3"), 
    #           data = df_3) +
    geom_point(aes(y = water_potential, x = lwc_mean, shape = time, color = "df_4"), 
               data = df_4) +
    geom_line(aes(y = water_potential, x = lwc_mean, group = tree_week, color = "df_4"), 
              data = df_4
              ) +
    scale_colour_manual(name = 'Week', 
         values =c("df_1" ="#122451", 
                   "df_2"="#62929a",
                  # "df_3"="#EC7E28",
                   "df_4"="#c969a8"
                   ), 
         labels = c('10',
                    '17',
                  #  '21',
                    '33')) +
    labs(y = "Water Potential (MPa)", 
       x = "Leaf Water Content (g)", 
       color= "Week", 
       shape = "Time"
       #caption = "triangles = predawn, circles = midday"
       ) +
  theme(
    #legend.position = c(.9, .35),
   # legend.position = "none",
     legend.position = "right",
  #strip.background = element_blank(),
  #strip.text.y = element_blank(), 
  #strip.text.x = element_text(size = 16), 
  axis.text.y = element_text(size = 12), 
  axis.text.x = element_text(size = 12), 
  #axis.ticks.y = element_blank(), 
  axis.title.y = element_text(size = 20), 
  axis.title.x = element_text(size = 20), 
 # axis.title.x = element_blank(),
  legend.title = element_text(size = 14), 
  legend.text = element_text(size = 14), 
# legend.position = "none"
  ) +
   xlim(.5,2) +
  scale_x_reverse()
nice_hydration_layered
  
ggsave(here("figures", "nice_hydration_layered"), nice_hydration_layered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Slopes of the formula: 

```{r, warning=T}
m_wk_rand <- lmer(water_potential ~ lwc_mean + (lwc_mean|tree) + (lwc_mean|week), data = wk_all )
```

Should we include site? 

```{r, include = F}
wk_all_sites <- wk_all %>% mutate(site = as.factor(site)) %>% 
  drop_na(site)

m_wk_rand_nosite <- lmer(water_potential ~ lwc_mean + (lwc_mean|tree) + (lwc_mean|week), data = wk_all_sites, REML = T)
#m_wk_rand_nosite

m_wk_rand_site <- lmer(water_potential ~ lwc_mean + (lwc_mean|tree) + (lwc_mean|week) + (1|site), data = wk_all_sites, REML = T)
#m_wk_rand_site

anova(m_wk_rand_nosite, m_wk_rand_site)

summary(m_wk_rand_nosite)
```

...NO, we do not need to include site. (p > .05)

What is the slope?

```{r, echo=FALSE}
#get estimates for each week: 

ran_list2 <- coef(m_wk_rand)

hyd_mod_df <- broom::tidy(m_wk_rand)


ran_df_hyd  <- as.data.frame(ran_list2[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_mean`, 
         -lwc_mean) %>%
  select(-`(Intercept)`)

#random error of each week: 

ran_err <- arm::se.ranef(m_wk_rand)

ran_err_df_hyd  <- as.data.frame(ran_err[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean`)%>% 
  select(-`(Intercept)`, 
         -lwc_mean) %>% 
  tibble::rownames_to_column("week") %>% 
  mutate(week = as.numeric(week))

#combine error with estimates: 

ran_df_week_hyd  <- bind_cols(ran_df_hyd , ran_err_df_hyd ) %>% 
  data_frame()
```

####Slopes, SE
```{r, echo=FALSE}
hyd_slopes <- ran_df_week_hyd %>%
  filter(!week %in% c(9)) %>%
 # filter(week %in% c(14, 17, 21, 29)) %>%
 # filter(term == "lwc_mean") %>%
  mutate(upr = slope + (std.error.slope),
         lwr = slope - (std.error.slope)) %>%
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(#x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
 axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
  legend.title = element_text(size = 18), 
 legend.position = "none"
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 18, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none") +
  #xlim(0, 40) +
  color_grad 
hyd_slopes

ggsave(here("figures", "nice_hydration_slopes"), hyd_slopes, device = "jpg", width = 5, height = 2.5, dpi = 300)
```

Random *intercepts* of each week:
```{r, echo=FALSE}
hyd_ints <- ran_df_week_hyd %>% 
  filter(!week %in% c(9)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18), 
 legend.position = "none"
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10,12, 14,15, 17, 18, 19, 21, 29, 33, 37))+
  color_grad
hyd_ints

ggsave(here("figures", "nice_hydration_ints"), hyd_ints, device = "jpg", width = 5, height = 2.5, dpi = 300)
```


####Slopes, bootstrapping

```{r}
hyd_slopes_bs_inds <- final_df_all %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "hydration, ind. trees") %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(#x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
 axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
  legend.title = element_text(size = 18), 
 legend.position = "none"
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 18, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none") +
  #xlim(0, 40) +
  color_grad 
hyd_slopes_bs_inds

ggsave(here("figures", "nice_hydration_slopes_bs_inds"), hyd_slopes_bs_inds, device = "jpg", width = 5, height = 2.5, dpi = 300)
```


#SPACE:

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wk_all_long %>% 
  filter(!week %in% c(9)) %>% 
  #filter(lwc_mean > .44) %>% 
  mutate(water_potential = water_potential) %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_lwc_mean = mean(lwc_mean, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(lwc_mean_centered = lwc_mean - mean_lwc_mean)
  # mutate(lwc_mean_centered = scale(lwc_mean,  scale=FALSE)) %>% 
  # filter(lwc_mean_centered < 4)
```


```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = lwc_mean_centered, 
            x = lwc_mean,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="none",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
      axis.title.x = element_blank(),
     axis.title.y = element_text(size = 20), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice

ggsave(here("figures", "nice_space"), space_nice, device = "jpg", width = 6, height = 4, dpi = 300)
```

```{r, warning = F, echo=FALSE}
#scaled
space_nice_centered <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_mean_centered, 
            #x = lwc_mean,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
        #legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 1))

space_nice_centered

ggsave(here("figures", "nice_space_centered"), space_nice_centered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Do we need to include site here? 

Centered lwc_mean:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc_mean_centered + (lwc_mean_centered|week) + (1|tree), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwc_mean_centered  + (lwc_mean_centered|week) + (1|tree) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

...YES, if centered. 

lwc_mean uncentered:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc_mean + (lwc_mean|week) + (1|tree), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwc_mean  + (lwc_mean|week) + (1|tree) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
...Yes? If using lwc_mean not centered. 



Visualize: 

###Slopes, MD, Centered:

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ lwc_mean_centered + (lwc_mean_centered|week) + (1|tree), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_mean_centered`, 
         -lwc_mean_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean_centered`)%>% 
  select(-`(Intercept)`, 
         -lwc_mean_centered) %>% 
  tibble::rownames_to_column("week") %>% 
  mutate(week = as.numeric(week))

# weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
# weeks_check

# weeks <- data_frame(1:10)
# weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29, 33) 

ran_df_week_3 <- bind_cols(ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()

ran_df_week_3 %>% 
 # mutate(week = as.factor(week)) %>% 
  mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  color_grad +
   # color_many_2 +
  guides(color = guide_legend(nrow = 2))
```

Intercepts - centered

```{r, echo=FALSE}
ran_df_week_3 %>% 
   mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
    color_grad +
  guides(color = guide_legend(nrow = 2))
```

##Slopes, MD, NOT Centered

Get slopes from random effects: 

NOTE: this includes site random effect, which the centered version does not need. 

```{r, echo=FALSE}
space_mod_4 <- lmer(water_potential ~ lwc_mean + (lwc_mean|week) + (1|tree) + (1|site), data =  wc_wk_centered_df, REML = T)

space_mod_df_4 <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod_4)

#ran_list2 <- coef(m_wk_rand)

ran_df_4 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_mean`, 
         -lwc_mean) %>%
  select(-`(Intercept)`)

ran_err_4 <- arm::se.ranef(space_mod_4)

ran_err_df_4 <- as.data.frame(ran_err_4[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean`)%>% 
  select(-`(Intercept)`, 
         -lwc_mean) %>% 
  tibble::rownames_to_column("week")

ran_df_week_4 <- bind_cols(ran_df_4, ran_err_df_4) %>% 
  #select(-`1:10`) %>% 
  data_frame()

space_slope <- ran_df_week_4 %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slope
```
Intercept - not centered

```{r, echo=FALSE}
ran_df_week_4 %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```


###Slopes, from bootsrapping: 

```{r}
space_slopes <- final_df_all %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "space") %>% 
   mutate(week = as.factor(week)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope - space") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title.y = element_text(size = 16),
      axis.title.x = element_blank(),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
space_slopes
```

###Predawn, centered


```{r, warning = F, eval = F}
wc_wk_centered_pd_df <- wc_qudo_df %>% 
  filter(time == "pd") %>% 
  group_by(week) %>% 
  mutate(mean_lwc_mean = mean(lwc_mean)) %>% 
  ungroup() %>% 
  mutate(lwc_mean_centered = lwc_mean - mean_lwc_mean)
  # mutate(lwc_mean_centered = scale(lwc_mean,  scale=FALSE)) %>% 
  # filter(lwc_mean_centered < 4)

#not scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  #filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_mean, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) 
#scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_mean_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Predawn MPa", 
       x = "lwc_mean (centered by week)", 
       color = "Week", 
       shape = "Site") +
  color_many

space_pd_df <- wc_wk_centered_pd_df %>%
  drop_na(site) %>%
  mutate(tree = as.factor(tree))

space_mod_site <- lmer(water_potential ~ lwc_mean_centered + (lwc_mean_centered|week) + (1|tree), data = space_pd_df, REML = F)
#summary(space_mod)

space_mod <- lmer(water_potential ~ lwc_mean_centered  + (lwc_mean_centered|week) + (1|tree) + (1|site), data = space_pd_df,  REML = F)
#summary(space_mod_site)

anova(space_mod, space_mod_site)

space_mod_pd_df <- broom.mixed::tidy(space_mod)
#space_mod_pd_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_pd_df <- as.data.frame(ran_list3[['week']])%>%
  mutate(estimate = `(Intercept)`,
         slope = `lwc_mean_centered`,
         -lwc_mean_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)
ran_err_pd_df <- as.data.frame(ran_err3[['week']]) %>%
  mutate(std.error = `(Intercept)`,
         std.error.slope = `lwc_mean_centered`)%>%
  select(-`(Intercept)`,
         -lwc_mean_centered)

weeks_check <- unique(space_pd_df$week) %>% as_data_frame()
#view(weeks_check)


#weeks <- data_frame(1:9)
#weeks$week <- c(9, 10, 11, 12, 14, 15, 17, 21, 29)

weeks <- tibble(1:11)
weeks$week <- unique(space_pd_df$week)
#weeks$week <- c(10, 14, 15, 17, 19, 21, 29, 33)

ran_pd_df_week <- bind_cols(weeks, ran_pd_df, ran_err_pd_df) %>%
 # select(-`1:9`) %>%
  data_frame()

ran_pd_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```


```{r, echo=FALSE}
ran_pd_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```

#TIME

```{r}
wc_qudo_df %>% 
  #filter(!week %in% c(9, 18, 19)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = lwc_mean, 
             x = as.factor(week), 
             #x = date,
            # color = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "lwc_mean", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE, warning = F}
time <- wc_qudo_df %>% 
  drop_na(week) %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_mean, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "lwc_mean", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2) +
  color_two_grey
time 

ggsave(here("figures", "nice_time"), time, device = "jpg", width = 4, height = 2, dpi = 300)
```



```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_mean, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "lwc_mean", 
       y = "Predawn MPa") +
  color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

All dates: 

Include site?

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc_mean + (1|week) + (lwc_mean|tree), data = space_df_nosite, REML = F)
#summary(space_mod)
AIC(space_mod)

space_mod_site <- lmer(water_potential ~ lwc_mean  + (1|week) + (lwc_mean|tree) + (1|site), data = space_df_nosite,  REML = F)

AIC(space_mod_site)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
####All time

```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")
  
time_mod <- lmer(water_potential ~ lwc_mean + (1|week) + (lwc_mean|tree), data = wc_qudo_md_df)
#time_mod <- lmer(water_potential ~ lwc_mean + (lwc_mean|tree), data = wc_qudo_md_df)
 
#with separate periods: 
time_season_mod <- lmer(water_potential ~ lwc_mean + time_season + (1|week) + (lwc_mean|tree), data = wc_qudo_md_df)

time_season_mod_df <- broom::tidy(time_season_mod)

MuMIn::r.squaredGLMM(time_mod)

summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = lwc_mean
         ) %>%
  select(-`(Intercept)`, 
          -lwc_mean)
tree_eff

ran_err_tree1 <- arm::se.ranef(time_mod)

ran_err_tree2 <- as.data.frame(ran_err_tree1[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc_mean
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree <- bind_cols(tree_eff, ran_err_tree2) %>% 
  #select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ lwc_mean)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

ran_df_tree %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = slope + (std.error), 
         lwr = slope - (std.error)) %>% 
  ggplot(aes(color= estimate)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = estimate))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ lwc_mean)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none", 
        axis.text.x = element_blank())#+
  #theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

####Just linear: 
```{r}
lin_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "after leafout")
  
  
lin_time_mod <- lmer(water_potential ~ lwc_mean + (1|week) + (lwc_mean|tree), data = lin_wc_qudo_md_df)
summary(lin_time_mod)

MuMIn::r.squaredGLMM(lin_time_mod)
```


```{r}
lin_ran_list <- coef(lin_time_mod)
lin_ran_list

lin_tree_eff <- as.data.frame(lin_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_mean`,
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -lwc_mean)
lin_tree_eff

lin_ran_err_tree <- arm::se.ranef(lin_time_mod)

lin_ran_err_tree <- as.data.frame(lin_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc_mean
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

lin_ran_df_tree_after <- bind_cols(lin_tree_eff, lin_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame() %>% 
  mutate(time_season = "After Leafout")

#With standard errors around estimates:

#intercetps 
lin_ran_df_tree_after%>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Intercepts, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 


lin_ran_df_tree_after %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

lin_ran_df_tree_after %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```
####Before leafout: 

```{r}
bef_wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "before leafout") %>% 
  drop_na(site)
  
  
bef_time_mod <- lmer(water_potential ~ lwc_mean + (1|week) + (lwc_mean|tree), data = bef_wc_qudo_md_df, REML = T)
summary(bef_time_mod)


MuMIn::r.squaredGLMM(bef_time_mod)
```


```{r}
bef_ran_list <- coef(bef_time_mod)

bef_tree_eff <- as.data.frame(bef_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_mean`, 
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -lwc_mean)
bef_tree_eff

bef_ran_err_tree <- arm::se.ranef(bef_time_mod)

bef_ran_err_tree <- as.data.frame(bef_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_mean`
         )%>% 
  select(-`(Intercept)`, 
         -lwc_mean
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

bef_ran_df_tree_before <- bind_cols(bef_tree_eff, bef_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()%>% 
  mutate(time_season = "Before Leafout")

bef_ran_df_tree_before %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc_mean") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, BEFORE LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

bef_ran_df_tree_before %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```

####Slopes, SE, pre- and post-

```{r}
ran_df_tree_before_vs_after <- bind_rows(bef_ran_df_tree_before, lin_ran_df_tree_after)

ef <- ran_df_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate(sd = sd(slope),
         slope = mean(slope), 
         mean_se = mean(std.error.slope),
        mean_std.error = mean(std.error),
        upr_sd = slope + mean_std.error,
        lwr_sd = slope - mean_std.error,
         upr = slope + mean_se,
         lwr = slope - mean_se,
         time_season = as.factor(time_season)) 
# %>% 
#   select(slope, upr, lwr, time_season, sd)

time_summary <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SE acrss all trees
            for each time frame", 
       x = "Time")
time_summary

time_summary_sd <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr_sd, x = time_season), size = 1) +
  geom_point(aes(y = lwr_sd, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr_sd, 
                   yend = upr_sd, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
            for each time frame", 
       x = "Time")
time_summary_sd

ggsave(here("figures", "time_summary_slopes"), time_summary, device = "jpg", width = 2.5, height = 3, dpi = 300)

```

##Slopes, bootstrapping - inds
 
```{r}
time_summary_bs_tree <- final_df_all %>% 
   filter(!week %in% c(9)) %>% 
  filter(analysis == "time, ind. tree") %>% 
   mutate(week = as.factor(week)) %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Bootstrapped slope and CI", 
       x = "Time")
time_summary_bs_tree


ggsave(here("figures", "time_summary_slopes_boot_tree"), time_summary_bs_tree, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

#Models

glanced mods

```{r}
glance_df <- bind_rows(space_glance <- broom.mixed::glance(space_mod) 
                       %>% mutate(mod = "space"),
                       hyd_glance <-  broom.mixed::glance(m_wk_rand) 
                       %>% mutate(mod = "hyd"),
                       time_glance <- broom.mixed::glance(time_season_mod)
                       %>% mutate(mod = "time"),
                       as_data_frame(r.squaredGLMM(space_mod)) 
                       %>% mutate(mod = "space"),
                       as_data_frame(r.squaredGLMM(m_wk_rand)) 
                       %>% mutate(mod = "hyd"),
                       as_data_frame(r.squaredGLMM(time_season_mod)) 
                       %>% mutate(mod = "time")) %>% 
  group_by(mod) %>% 
  fill(c(R2m, R2c), .direction = "downup") %>% 
  distinct() %>% 
  drop_na(df.residual)
glance_df
```

Tidy mods
```{r}
lwc_mods <- bind_rows(space_mod_df <- space_mod_df %>% 
                        mutate(mod = "space"), 
                      hyd_mod_df <- hyd_mod_df %>% 
                        mutate(mod = "hyd"),
                      time_season_mod_df <- 
                        hyd_mod_df %>% mutate(mod= "time")) %>% 
  bind_rows(glance_df) %>% 
    mutate(var = "lwc")

lwc_mods

write_csv(lwc_mods, here::here("processed-data", "lwc_mods.csv"))
```






