---
title: "Establishing relationships between lwa_g_cm2 and MPa, Part 2"
author: "Indra Boving"
date: "11/9/2022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#install.packages("")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

source(here::here("scripts", "scripts_functions", "figure_info.R"))

#datver <- "01052023"
#dataversion <- paste0("Data_", datver)
```

```{r, echo=F}
#wc_all_raw <- read_csv(here("processed-data", paste0("lwa_g_cm2_LFM_WP_dates",datver,".csv")), show_col_types = FALSE) %>% 
wc_all_raw <- read_csv(here("processed-data", paste0("wp_wc_rwc_",datver,".csv")), show_col_types = FALSE) %>% 
  filter(species == "blue oak") 

wc_qudo_df <- wc_all_raw %>% 
   filter(#week > 15, 
        # lwa_g_cm2_mean < 5, 
         #lwa_g_cm2_mean > 0
         ) %>% 
  filter(!(week == 29 & lwa_g_cm2 > 1)) %>% 
  mutate(lwa_g_cm2 = lwa_g_cm2) %>% 
  group_by(tree, week, time) %>% 
  mutate(water_potential = mean(mpa_mean), 
         tree_factor = as.factor(tree)) %>% 
  ungroup() %>% 
  mutate(week = case_when(
    week %in% c(13) ~ 14,
    week %in% c(11) ~ 10,
    TRUE ~ week
  )) %>%
  select(week, time, lwa_g_cm2, water_potential, date_wp,
         tree, tree_factor, plot, site, species) %>% 
  distinct() %>% 
  filter(!week == 9)
```

What is the linear portion? 

```{r}
wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  ggplot(aes(y = alas_cm2_per_mm2, 
             x = week, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  color_very_many +
  labs(title = "Al:As", 
       y = "Al:As (cm2/mm2)", 
       x = "Week", 
       color = "Week")
```


```{r}
wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  filter(lma_g_cm2 < 0.05) %>% 
  ggplot(aes(y = lma_g_cm2, 
             x = week, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  color_many +
  labs(title = "Leaf Mass per Area", 
       y = "LMA (g/cm2)", 
       x = "Week", 
       color = "Week")
```

Week 17 looks like a goot cutoff:
```{r, echo=F}
wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)
```

From what weeks do we have the most trees?
```{r, echo=F}
wc_qudo_df %>% 
  select(week, time, tree, lwa_g_cm2) %>% 
  drop_na(lwa_g_cm2) %>% 
  unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") + 
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "lwa_g_cm2 counts") +
  color_fill
```

```{r, echo=F}
wc_qudo_df %>% 
    select(week, time, tree, water_potential) %>% 
  drop_na(water_potential) %>% 
 # unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") +
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "MPa counts") +
  color_fill
```
A: week 17, 21, 29, 10


#Hydration per week: 

MPa ~ lwa_g_cm2 + (lwa_g_cm2|tree) + (1|wk)

```{r, echo=FALSE}
wc_qudo_df %>% 
  #filter(week %in% c(10, 13, 17, 21, 29)) %>% 
  filter(lwa_g_cm2 < .03) %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2, 
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  facet_wrap(~week, scales = "free") +
 # theme(legend.position = "none") +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "lwa_g_cm2")
```

```{r, warning = F}
wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(lwa_g_cm2, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(lwa_g_cm2_md, lwa_g_cm2_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk_all_long_lwa_g_cm2 <- wk_all_wide %>% 
  drop_na(lwa_g_cm2_pd, lwa_g_cm2_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = lwa_g_cm2_pd, 
         md = lwa_g_cm2_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "lwa_g_cm2") %>% 
  select(-lwa_g_cm2_pd, -lwa_g_cm2_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(lwa_g_cm2_pd, lwa_g_cm2_md, water_potential_md, water_potential_pd) %>% 
  select(-lwa_g_cm2_md, -lwa_g_cm2_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_lwa_g_cm2) %>% 
  distinct() %>% 
 # select(-lwa_g_cm2_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(lwa_g_cm2 = mean(lwa_g_cm2, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T), 
            site = site)
```

###nice hyd
```{r, echo=FALSE, fig.height= 5, fig.width= 2}
wk_figs <- wk_all_long %>% 
  filter(week %in% c(10, 14, 17, 19, 21, 29, 33, 37), 
         lwa_g_cm2 < .02, 
         lwa_g_cm2 > 0
         ) %>% 
  mutate(week_nice = case_when(
    week == 10 ~ "Week 10", 
    week == 14 ~ "Week 14", 
    week == 17 ~ "Week 17", 
    week == 19 ~ "Week 19", 
    week == 21 ~ "Week 21", 
    week == 29 ~ "Week 29",
    week == 33 ~ "Week 33",
    week == 37 ~ "Week 37"
  )) 

wk_figs_labels <-
  data.frame(
    label = c('10', '11', '17', '19', '21', '29', '33', '37'),
    week_nice = c(
      "Week 10",
      "Week 14",
      "Week 17",
      "Week 19",
      "Week 21",
      "Week 29",
      "Week 33",
      "Week 37"
    )
  )

nice_hyd_lwa <- wk_figs %>% 
  #filter(!(week == 29 & lwa_g_cm2 > 1)) %>% 
  ggplot(aes(y = -1*water_potential, 
             x = lwa_g_cm2,
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time,
                 color = as.factor(tree)
                 ), 
             size = 2, 
             alpha = .6) + 
  geom_smooth(method = "lm",
              se = F, 
              alpha = .3) +
  facet_wrap(~week_nice, 
             ncol = 1,
              strip.position="top"
            # scales = "free"
             ) +
  #annotate("text", x= .5, y = 6, label =unique(wk_figs$week_nice))+
 # theme(legend.position = "none") +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text = element_text(size=9, lineheight=.3),
     # panel.spacing = unit(0, "lines"),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
       axis.title = element_text(size = 16), 
    # panel.margin = unit(c(-0.2,0, -0.2,0), "lines")
    ) +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "Leaf Water/Area (g/cm2)", 
       #caption = "triangles = predawn, circles = midday"
       )# +
 # xlim(.5,2) #+
  #geom_text(aes(label = label), data = wk_figs_labels, x= .5, y = 6) 

nice_hyd_lwa

ggsave(here("figures", "nice_hydration_lwa"), nice_hyd_lwa, device = "jpg", width = 3, height = 9, dpi = 300)
```

Slopes of the formula: 

```{r, warning=T}
m_wk_rand <- lmer(-1*water_potential ~ lwa_g_cm2 + (lwa_g_cm2|tree) + (lwa_g_cm2|week), data = wk_all )
#m_wk_rand
#summary(m_wk_rand)
```

Should we include site? 

```{r, include = F}
wk_all_sites <- wk_all %>% mutate(site = as.factor(site)) %>% 
  drop_na(site)

m_wk_rand_nosite <- lmer(-1*water_potential ~ lwa_g_cm2 + (lwa_g_cm2|tree) + (lwa_g_cm2|week), data = wk_all_sites, REML = T)
#m_wk_rand_nosite

m_wk_rand_site <- lmer(-1*water_potential ~ lwa_g_cm2 + (lwa_g_cm2|tree) + (lwa_g_cm2|week) + (1|site), data = wk_all_sites, REML = T)
#m_wk_rand_site

anova(m_wk_rand_nosite, m_wk_rand_site)
```

...NO, we do not need to include site. (p > .05)


What is the slope?

```{r, echo=FALSE}
grand_slope <- broom.mixed::tidy(m_wk_rand)
#grand_slope

#ran_list <- ranef(m_wk_rand)

ran_list2 <- coef(m_wk_rand)

ran_df <- as.data.frame(ran_list2[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwa_g_cm2`, 
         -lwa_g_cm2) %>%
  select(-`(Intercept)`)

ran_err <- arm::se.ranef(m_wk_rand)
ran_err_df <- as.data.frame(ran_err[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwa_g_cm2`)%>% 
  select(-`(Intercept)`, 
         -lwa_g_cm2)  %>% 
  tibble::rownames_to_column("week")

# week_ranerr <- nrow(ran_err_df)
# 
# #Comment the below based on if we're combining weeks (e.g. week 13 and 14, or week 10 and 11)
# weeks <- tibble(1:5)
# weeks$week <- c(14, 17, 21, 29, 37) 

#weeks <- tibble(1:11)
#weeks$week <- c(9, 10, 11, 13, 14, 15, 17, 18, 19, 21, 29) 

ran_df_week <- bind_cols(weeks, ran_df, ran_err_df) %>% 
  data_frame()
```

Are the slopes significantly different from each other? 

```{r}
ranef(m_wk_rand, condVar=T)

sjPlot::plot_model(m_wk_rand, type = "re", show.p = T)
```


Random slopes of each week: 

####SLOPES
```{r, echo=FALSE}
hyd_slopes <- ran_df_week %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Slope",
       title = "Predawn-Midday Slopes") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 15), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 16), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 14,15, 17, 18, 19, 21, 29, 33)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none") +
  color_grad 
hyd_slopes

ggsave(here("figures", "nice_hydration_slopes"), hyd_slopes, device = "jpg", width = 5, height = 2.5, dpi = 300)
```



Random intercepts of each week:


```{r, echo=FALSE}
ran_df_week %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  color_grad
```


#Space

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wk_all_long %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_lwa_g_cm2 = mean(lwa_g_cm2, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(lwa_g_cm2_centered = lwa_g_cm2 - mean_lwa_g_cm2) %>% 
  distinct()
  # mutate(lwa_g_cm2_centered = scale(lwa_g_cm2,  scale=FALSE)) %>% 
  # filter(lwa_g_cm2_centered < 4)
```



####SPACE - fig: 

```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
 # drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Leaf Water/Area", 
       color = "Week", 
       shape = "Site") +
  color_weeks +
  guides(color = guide_legend(nrow = 1))
space_nice

ggsave(here("figures", "nice_space_lwa"), space_nice, device = "jpg", width = 4, height = 2, dpi = 300)
```

Do we need to include site here? 

```{r}
space_df_nosite <- wc_wk_centered_df 
#%>% 
  #drop_na(site)

space_mod <- lmer(water_potential ~ lwa_g_cm2_centered + (lwa_g_cm2_centered|week) + (1|tree), data = space_df_nosite, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwa_g_cm2_centered  + (lwa_g_cm2_centered|week) + (1|tree) + (1|site), data = space_df_nosite,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

...NO. 

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ lwa_g_cm2_centered + (lwa_g_cm2_centered|week) + (1|tree), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwa_g_cm2_centered`, 
         -lwa_g_cm2_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwa_g_cm2_centered`)%>% 
  select(-`(Intercept)`, 
         -lwa_g_cm2_centered)  %>% 
  tibble::rownames_to_column("week")

# weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
# weeks_check
# 
# weeks <- data_frame(1:4)
# weeks$week <- c(14, 17, 21, 29) 

ran_df_week <- bind_cols(weeks, ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()
```

Visualize: 

####SLOPES - space

```{r, echo=FALSE}
ran_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```


```{r, echo=FALSE}
ran_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```

###Predawn


```{r, warning = F}
wc_wk_centered_pd_df <- wc_qudo_df %>% 
  filter(time == "pd") %>% 
  group_by(week) %>% 
  mutate(mean_lwa_g_cm2 = mean(lwa_g_cm2)) %>% 
  ungroup() %>% 
  mutate(lwa_g_cm2_centered = lwa_g_cm2 - mean_lwa_g_cm2)
  # mutate(lwa_g_cm2_centered = scale(lwa_g_cm2,  scale=FALSE)) %>% 
  # filter(lwa_g_cm2_centered < 4)

#not scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  #filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) 
#scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Predawn MPa", 
       x = "lwa_g_cm2 (centered by week)", 
       color = "Week", 
       shape = "Site") +
  color_many
```

```{r}
space_pd_df <- wc_wk_centered_pd_df %>% 
  drop_na(site)

space_mod_site <- lmer(water_potential ~ lwa_g_cm2_centered + (lwa_g_cm2_centered|week) + (1|tree), data = space_pd_df, REML = F)
#summary(space_mod)

space_mod <- lmer(water_potential ~ lwa_g_cm2_centered  + (lwa_g_cm2_centered|week) + (1|tree) + (1|site), data = space_pd_df,  REML = F)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod_pd_df <- broom.mixed::tidy(space_mod)
#space_mod_pd_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_pd_df <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwa_g_cm2_centered`, 
         -lwa_g_cm2_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)
ran_err_pd_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwa_g_cm2_centered`)%>% 
  select(-`(Intercept)`, 
         -lwa_g_cm2_centered)  %>% 
  tibble::rownames_to_column("week")

# weeks_check <- unique(space_pd_df$week) %>% as_data_frame() 
# 
# #weeks <- data_frame(1:9)
# #weeks$week <- c(9, 10, 11, 12, 14, 15, 17, 21, 29) 
# 
# weeks <- tibble(1:8)
# weeks$week <- c(10, 14, 15, 17, 19, 21, 29, 33) 

ran_pd_df_week <- bind_cols(weeks, ran_pd_df, ran_err_pd_df) %>% 
 # select(-`1:9`) %>% 
  data_frame()
```


####SLOPES

Visualize: 

```{r, echo=FALSE}
ran_pd_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```


```{r, echo=FALSE}
ran_pd_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```

#Time

```{r}
wc_qudo_df %>% 
  filter(!week %in% c(9, 18, 19)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = lwa_g_cm2, 
             x = as.factor(week), 
             #x = date,
            # color = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "lwa_g_cm2", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE}
time_lwa <- wc_qudo_df %>% 
  drop_na(week) %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2, 
             color = as.factor(tree), 
             size = week,
             show.legend = FALSE)) +
  geom_point(#aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "lwa_g_cm2", 
       y = "Midday MPa") +
  color_many +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water/Area (g/cm2)", 
       color = "Week", 
      # shape = "Site"
       ) +
  color_very_many +
  guides(color = guide_legend(nrow = 2))
time_lwa

ggsave(here("figures", "nice_time_lwa"), time, device = "jpg", width = 4, height = 2, dpi = 300)
```


```{r, echo=FALSE}
wc_qudo_df %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "lwa_g_cm2", 
       y = "Water Potential") +
  facet_wrap(~time, ncol=1) +
  color_very_many +
  theme(legend.position = "none") +
  xlim(0.005, .035)
```

```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = lwa_g_cm2, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "lwa_g_cm2", 
       y = "Predawn MPa") +
  color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")
  
time_mod <- lmer(water_potential ~ lwa_g_cm2 + (lwa_g_cm2|week) + (1|tree), data = wc_qudo_md_df)
#summary(time_mod)
```


```{r, echo=FALSE, include = F}
#ran_list <- ranef(time_mod)
ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
        # slope = `lwa_g_cm2`
         ) %>%
  select(-`(Intercept)`, 
          -lwa_g_cm2)
tree_eff

ran_err_tree <- arm::se.ranef(time_mod)
ran_err_tree <- as.data.frame(ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
        # std.error.slope = `lwa_g_cm2`
         )%>% 
  select(-`(Intercept)`, 
        # -lwa_g_cm2
         )

inds<- data_frame(1:54)
inds$tree <- c(unique(wc_qudo_md_df$tree))

ran_df_tree <- bind_cols(inds, tree_eff, ran_err_tree) %>% 
 # select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwa_g_cm2") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ lwa_g_cm2)") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 
```

Predawn slopes for each individual: 

```{r, echo=FALSE}
wc_qudo_pd_df <- wc_qudo_df %>% 
  filter(time == "pd")

time_mod <- lmer(water_potential ~ lwa_g_cm2 + (lwa_g_cm2|week) + (1|tree), data = wc_qudo_pd_df)
summary(time_mod)
```


