---
title: "Establishing relationships between LWC and MPa, Part 2"
author: "Indra Boving"
date: "11/9/2022"
output:
  html_document: default
  word_document: default
---

#setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#install.packages("")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)

select = dplyr::select

source(here::here("scripts", "scripts_functions", "figure_info.R"))

#datver <- "01052023"
dataversion <- paste0("Data_", datver)
```

```{r, echo=F}
wc_all_raw <- read_csv(here("processed-data", paste0("LWC_LFM_WP_dates",datver,".csv")), show_col_types = FALSE) %>% 
  filter(species == "blue oak") %>% 
  mutate(lwc_mean = lwc_mean_combined)

wc_qudo_df <- wc_all_raw %>% 
   filter(#week > 15, 
        # lwc_mean < 5, 
         #lwc_mean > 0
         ) %>% 
  filter(!(week == 29 & lwc_mean > 1)) %>% 
  mutate(lwc = lwc_mean) %>% 
  group_by(tree, week, time) %>% 
  mutate(water_potential = mean(mpa_mean), 
         tree_factor = as.factor(tree)) %>% 
  ungroup() %>% 
  mutate(week = case_when(
    week %in% c(13) ~ 14, 
    week %in% c(11) ~ 10, 
    TRUE ~ week
  )) %>% 
  select(week, time, lwc, water_potential,
         tree, tree_factor, plot, site, species, date_wp) %>% 
  distinct()
```

What is the linear portion? 
```{r}
alas_df_analysis <- read_csv(here::here("processed-data", paste0("alas_leaf_area_df_week",datver,".csv")))

alas_df_analysis %>% 
  filter(species == "B") %>% 
  ggplot(aes(y = alas, 
             x = date_alas, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  labs(title = "Alas")

alas_df_analysis %>% 
  filter(species == "B") %>% 
  ggplot(aes(y = lma_g_cm2, 
             x = date_alas, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  labs(title = "LMA")
```

Week 17 looks like a goot cutoff:
```{r, echo=F}
wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)
```

From what weeks do we have the most trees?
```{r, echo=F}
wc_qudo_df %>% 
  select(week, time, tree, lwc) %>% 
  unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") + 
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "LWC counts") +
  color_fill
```

```{r, echo=F}
wc_qudo_df %>% 
    select(week, time, tree, water_potential) %>% 
 # unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") +
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "MPa counts") +
  color_fill
```
A: week 17, 21, 29, 10


#Hydration per week: 

MPa ~ lwc + (lwc|tree) + (1|wk)

```{r, echo=FALSE}
wc_qudo_df %>% 
  #filter(week %in% c(10, 13, 17, 21, 29)) %>% 
  filter(lwc < 5) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  facet_wrap(~week, scales = "free") +
 # theme(legend.position = "none") +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "LWC")
```
What we want to do, but just with week 10: 
```{r}
wk10 <- wc_qudo_df %>% 
  filter(week == 10)

wk10_wide <- wk10 %>% 
  pivot_wider(names_from=time, 
              values_from = c(lwc, water_potential)) %>% 
    dplyr::group_by(tree) %>%
  fill(c(lwc_md, lwc_pd, water_potential_pd, water_potential_md, date_wp), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk10_long_lwc <- wk10_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = lwc_pd, 
         md = lwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "lwc") %>% 
  select(-lwc_pd, -lwc_md)

wk10_long_mpa <- wk10_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-lwc_md, -lwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk10_long <- merge(wk10_long_mpa, wk10_long_lwc)
```


```{r}
wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  pivot_wider(names_from=time, 
              values_from = c(lwc, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(lwc_md, lwc_pd, water_potential_pd, water_potential_md, date_wp), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk_all_long_lwc <- wk_all_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = lwc_pd, 
         md = lwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "lwc") %>% 
  select(-lwc_pd, -lwc_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-lwc_md, -lwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_lwc) %>% 
  distinct() %>% 
  select(-lwc_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(lwc = mean(lwc), 
            water_potential = mean(water_potential))
```

###nice hyd
```{r, echo=FALSE, fig.height= 5, fig.width= 2}
wk_figs <- wk_all_long %>% 
  filter(week %in% c(10, 14, 17, 21, 29), 
         lwc < 6, 
         lwc > 0
         ) %>% 
  mutate(week_nice = case_when(
    week == 10 ~ "Week 10", 
    week == 14 ~ "Week 14", 
    week == 17 ~ "Week 17", 
    week == 21 ~ "Week 21", 
    week == 29 ~ "Week 29"
  )) 

wk_figs_labels <- data.frame(label = c('10', '11', '17', '21', '29'), 
                             week_nice = c("Week 10", "Week 14", "Week 17", 
                                           "Week 21", "Week 29"))

nice_hyd <- wk_figs %>% 
  filter(!(week == 29 & lwc > 1)) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc,
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time,
                 color = as.factor(tree)
                 ), 
             size = 2, 
             alpha = .6) + 
  geom_smooth(method = "lm",
              se = F, 
              alpha = .3) +
  facet_wrap(~week_nice, 
             ncol = 1,
              strip.position="top"
            # scales = "free"
             ) +
  #annotate("text", x= .5, y = 6, label =unique(wk_figs$week_nice))+
 # theme(legend.position = "none") +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text = element_text(size=9, lineheight=.3),
     # panel.spacing = unit(0, "lines"),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
       axis.title = element_text(size = 16), 
    # panel.margin = unit(c(-0.2,0, -0.2,0), "lines")
    ) +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "LWC", 
       #caption = "triangles = predawn, circles = midday"
       ) +
  xlim(.5,2) #+
  #geom_text(aes(label = label), data = wk_figs_labels, x= .5, y = 6) 

nice_hyd

ggsave(here("figures", "nice_hydration"), nice_hyd, device = "jpg", width = 3, height = 6, dpi = 300)
```


```{r, echo=FALSE}
wk_all  %>% 
  filter(week %in% c(17)) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  facet_wrap(~week, scales = "free") +
  theme(legend.position = "none") +
  color_very_many
```

```{r, include=F}
wc_lm_hyd_df <- wk_all 

for (i in unique(wc_lm_hyd_df$week)) {
  
  df <- wc_lm_hyd_df %>% 
    filter(week == i)
  
  p <- df %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  #theme(legend.position = "none") +
  labs(title = i)
  
  if (!is.null(p)) plot(p)
  
}
```


```{r, warning=F, echo=FALSE, include = F}
wk_all  %>% 
  ggplot(aes(y= water_potential, 
             x = lwc, 
             color = interaction(tree, week), 
             shape = time)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  theme(legend.position = "none") 
```

Slopes of the formula: 

```{r, warning=T}
library(nlme)
m_wk_rand <- lmer(water_potential ~ lwc + (lwc|tree) + (lwc|week), data = wk_all )
#m_wk_rand
#summary(m_wk_rand)
```

Should we include site? 

```{r, include = F}
wk_all_sites <- wk_all %>% mutate(site = as.factor(site)) %>% 
  drop_na(site)

m_wk_rand_nosite <- lmer(water_potential ~ lwc + (lwc|tree) + (lwc|week), data = wk_all_sites, REML = T)
#m_wk_rand_nosite

m_wk_rand_site <- lmer(water_potential ~ lwc + (lwc|tree) + (lwc|week) + (1|site), data = wk_all_sites, REML = T)
#m_wk_rand_site

anova(m_wk_rand_nosite, m_wk_rand_site)
```

...NO, we do not need to include site.


What is the slope?

```{r, echo=FALSE}
grand_slope <- broom.mixed::tidy(m_wk_rand)
#grand_slope

#ran_list <- ranef(m_wk_rand)

ran_list2 <- coef(m_wk_rand)

ran_df <- as.data.frame(ran_list2[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc`, 
         -lwc) %>%
  select(-`(Intercept)`)

ran_err <- arm::se.ranef(m_wk_rand)
ran_err_df <- as.data.frame(ran_err[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc`)%>% 
  select(-`(Intercept)`, 
         -lwc)

week_ranerr <- nrow(ran_err_df)

#Comment the below based on if we're combining weeks (e.g. week 13 and 14, or week 10 and 11)
weeks <- tibble(1:9)
weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29) 

#weeks <- tibble(1:11)
#weeks$week <- c(9, 10, 11, 13, 14, 15, 17, 18, 19, 21, 29) 

ran_df_week <- bind_cols(weeks, ran_df, ran_err_df) %>% 
  data_frame()
```

Random slopes of each week: 

####SLOPES
```{r, echo=FALSE}
hyd_slopes <- ran_df_week %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 16), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 11,14,15, 17, 18, 19, 21, 29)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none") +
  color_grad
hyd_slopes

ggsave(here("figures", "nice_hydration_slopes"), hyd_slopes, device = "jpg", width = 4, height = 2, dpi = 300)
```



Random intercepts of each week:
```{r, echo=FALSE}
ran_df_week %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  color_grad
```


#Space

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_lwc = mean(lwc, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(lwc_centered = lwc - mean_lwc)
  # mutate(lwc_centered = scale(lwc,  scale=FALSE)) %>% 
  # filter(lwc_centered < 4)
```



####SPACE - fig: 

```{r, warning = F, echo=FALSE}
#not scaled
wc_wk_centered_df %>% 
  drop_na(site) %>% 
  #filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F)
```


```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
            # aes (shape = site)
             ) +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text = element_text(size=9, lineheight=.3),
     # panel.spacing = unit(0, "lines"),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
       axis.title = element_text(size = 16), 
    # panel.margin = unit(c(-0.2,0, -0.2,0), "lines")
    ) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "LWC (centered by week)", 
       color = "Week", 
       shape = "Site") +
  color_many
space_nice

ggsave(here("figures", "nice_space"), space_nice, device = "jpg", width = 4, height = 2, dpi = 300)
```
Do we need to include site here? 
```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data = space_df, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwc_centered  + (lwc_centered|week) + (1|tree) + (1|site), data = space_df,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

...NO. 

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_centered`, 
         -lwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)
ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_centered`)%>% 
  select(-`(Intercept)`, 
         -lwc_centered)

weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
weeks_check

weeks <- data_frame(1:8)
weeks$week <- c(10, 14, 15, 17, 18, 19, 21, 29) 

ran_df_week <- bind_cols(weeks, ran_df, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()
```

Visualize: 

####SLOPES - space

```{r, echo=FALSE}
ran_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 16), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
#  geom_hline(yintercept = 0, linetype="dotted") + 
  #scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none") +
    color_many
```


```{r, echo=FALSE}
ran_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  color_many
```


###Predawn
```{r, warning = F}
wc_wk_centered_pd_df <- wc_qudo_df %>% 
  filter(time == "pd") %>% 
  group_by(week) %>% 
  mutate(mean_lwc = mean(lwc)) %>% 
  ungroup() %>% 
  mutate(lwc_centered = lwc - mean_lwc)
  # mutate(lwc_centered = scale(lwc,  scale=FALSE)) %>% 
  # filter(lwc_centered < 4)

#not scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  #filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) 
#scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Predawn MPa", 
       x = "LWC (centered by week)", 
       color = "Week", 
       shape = "Site") +
  color_many
```

```{r}
space_pd_df <- wc_wk_centered_pd_df %>% 
  drop_na(site)

space_mod_site <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data = space_pd_df, REML = F)
#summary(space_mod)

space_mod <- lmer(water_potential ~ lwc_centered  + (lwc_centered|week) + (1|tree) + (1|site), data = space_pd_df,  REML = F)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod_pd_df <- broom.mixed::tidy(space_mod)
#space_mod_pd_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_pd_df <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_centered`, 
         -lwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)
ran_err_pd_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_centered`)%>% 
  select(-`(Intercept)`, 
         -lwc_centered)

weeks_check <- unique(space_pd_df$week) %>% as_data_frame() 

weeks <- data_frame(1:9)
weeks$week <- c(9, 10, 11, 12, 14, 15, 17, 21, 29) 

ran_pd_df_week <- bind_cols(weeks, ran_pd_df, ran_err_pd_df) %>% 
  select(-`1:9`) %>% 
  data_frame()
```

Visualize: 

```{r, echo=FALSE}
ran_pd_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
#  geom_hline(yintercept = 0, linetype="dotted") + 
  #scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none") +
    color_many
```


```{r, echo=FALSE}
ran_pd_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  color_many
```

#Time

```{r}
wc_qudo_df %>% 
  filter(!week %in% c(9, 18, 19)) %>% 
  ggplot(aes(y = lwc, 
             x = as.factor(week), 
             #x = date,
            # color = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "LWC", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(week), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Midday MPa") +
  color_many
```

```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Midday MPa") +
  color_very_many +
  theme(legend.position = "none")
```
```{r, echo=FALSE}
wc_qudo_df %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Water Potential") +
  facet_wrap(~time, ncol=1) +
  color_very_many +
  theme(legend.position = "none")
```

```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Predawn MPa") +
  color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")
  
time_mod <- lmer(water_potential ~ lwc + (lwc|week) + (1|tree), data = wc_qudo_md_df)
summary(time_mod)
```


```{r, echo=FALSE, include = F}
#ran_list <- ranef(time_mod)
ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
        # slope = `lwc`
         ) %>%
  select(-`(Intercept)`, 
          -lwc)
tree_eff

ran_err_tree <- arm::se.ranef(time_mod)
ran_err_tree <- as.data.frame(ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
        # std.error.slope = `lwc`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc
         )

inds<- data_frame(1:47)
inds$tree <- c(unique(wc_qudo_md_df$tree))

ran_df_tree <- bind_cols(inds, tree_eff, ran_err_tree) %>% 
  select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ LWC)") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 
```

Predawn slopes for each individual: 

```{r, echo=FALSE}
wc_qudo_pd_df <- wc_qudo_df %>% 
  filter(time == "pd")

time_mod <- lmer(water_potential ~ lwc + (lwc|week) + (1|tree), data = wc_qudo_pd_df)
summary(time_mod)
```


```{r, echo=FALSE, include = F}
#ran_list <- ranef(time_mod)
# ran_list <- coef(time_mod)
# 
# tree_eff <- as.data.frame(ran_list[['week']]) %>% 
#   mutate(estimate = `(Intercept)`, 
#          slope = `lwc`) %>%
#   select(-`(Intercept)`, 
#           -lwc)
# tree_eff
# 
# ran_err_tree <- arm::se.ranef(time_mod)
# ran_err_tree <- as.data.frame(ran_err_tree[['week']]) %>% 
#   mutate(std.error = `(Intercept)`, 
#          std.error.slope = `lwc`)%>% 
#   select(-`(Intercept)`, 
#          -lwc)
# 
# inds<- data_frame(1:8)
# inds$tree <- c(unique(wc_qudo_pd_df$week))
# 
# ran_df_tree <- bind_cols(inds, tree_eff, ran_err_tree) %>% 
#   select(-`1:8`) %>% 
#   data_frame()
# 
# ran_df_tree %>% 
#   mutate(tree = as.factor(week)) %>% 
#  # filter(tree %in% c(14, 17, 21, 29)) %>% 
#  # filter(term == "lwc") %>% 
#   mutate(upr = slope + (std.error.slope/2), 
#          lwr = slope - (std.error.slope/2)) %>% 
#   ggplot(aes(color= tree)
#     ) + 
#   geom_point(aes(y = slope ,x = tree), size =3) +
#     geom_point(aes(y = upr, x = tree), size = 1) +
#   geom_point(aes(y = lwr, x = tree), size = 1) +
#   #geom_line(aes(group = tree, y = tree, x = upr)) +
#   geom_segment(aes(y= lwr, 
#                    yend = upr, 
#                    x = tree, 
#                    xend = tree, 
#                    color = tree))+
#   labs(x = "Week", 
#        color = "Week", 
#        y = "Slope") +
#    # facet_wrap(~y_var_name, scales = "free") + 
# theme(
#   strip.background = element_blank(),
#   strip.text.y = element_blank(), 
#   strip.text.x = element_text(size = 18), 
#  # axis.text.y = element_blank(), 
#   #axis.ticks.y = element_blank(), 
#   axis.title = element_text(size = 20), 
#   legend.title = element_text(size = 18)
#   ) +
#   geom_hline(yintercept = 0, linetype="dotted") + 
#  # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
#   theme(legend.position = "none")+
#   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```
