---
title: "Establishing relationships between LWC and MPa, Part 2"
author: "Indra Boving"
date: "11/9/2022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#install.packages("")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

source(here::here("scripts", "scripts_functions", "figure_info.R"))

#datver <- "01052023"
dataversion <- paste0("Data_", datver)
```

```{r, echo=F}
#wc_all_raw <- read_csv(here("processed-data", paste0("LWC_LFM_WP_dates",datver,".csv")), show_col_types = FALSE) %>% 
wc_all_raw <- read_csv(here("processed-data", paste0("wp_wc_rwc_",datver,".csv")), show_col_types = FALSE) %>% 
  filter(species == "blue oak") 

wc_qudo_df <- wc_all_raw %>% 
   filter(#week > 15, 
        # lwc_mean < 5, 
         #lwc_mean > 0
         ) %>% 
  filter(!(week == 29 & lwc_mean > 1)) %>% 
  mutate(lwc = lwc_mean) %>% 
  group_by(tree, week, time) %>% 
  mutate(water_potential = mean(mpa_mean), 
         tree_factor = as.factor(tree)) %>% 
  ungroup() %>% 
  mutate(week = case_when(
    week %in% c(13) ~ 14,
    week %in% c(11) ~ 10,
    TRUE ~ week
  )) %>%
  select(week, time, lwc, water_potential, date_wp,
         tree, tree_factor, plot, site, species) %>% 
  distinct() %>% 
  filter(!week == 9) %>% 
  mutate(time_season = case_when(
    week <= 17 ~ "before leafout", 
    week > 17 ~ "after leafout", 
    TRUE ~ as.character("none")
  ))
```

What is the linear portion? 

```{r}
wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  ggplot(aes(y = alas_cm2_per_mm2, 
             x = week, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  labs(title = "Alas")

wc_all_raw %>% 
  filter(species == "blue oak") %>% 
  filter(lma_g_cm2 < 0.05) %>% 
  ggplot(aes(y = lma_g_cm2, 
             x = week, 
             color = as.factor(week)
             )) +
  geom_jitter() +
  labs(title = "LMA")
```

Week 17 looks like a goot cutoff:
```{r, echo=F}
wc_lm_df <- wc_qudo_df %>% 
  filter(week > 17)
```

From what weeks do we have the most trees?
```{r, echo=F}
wc_qudo_df %>% 
  select(week, time, tree, lwc) %>% 
  drop_na(lwc) %>% 
  unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") + 
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "LWC counts") +
  color_fill
```

```{r, echo=F}
wc_qudo_df %>% 
    select(week, time, tree, water_potential) %>% 
  drop_na(water_potential) %>% 
 # unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") +
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "MPa counts") +
  color_fill
```
A: week 17, 21, 29, 10


#**Hydration per week: 

MPa ~ lwc + (lwc|tree) + (1|wk)

```{r, echo=FALSE}
wc_qudo_df %>% 
  #filter(week %in% c(10, 13, 17, 21, 29)) %>% 
  filter(lwc < 5) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  facet_wrap(~week, scales = "free") +
 # theme(legend.position = "none") +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "LWC")
```

```{r, warning = F}
wk_all <- wc_qudo_df 

wk_all_wide <- wk_all %>% 
  drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(lwc, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(lwc_md, lwc_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk_all_long_lwc <- wk_all_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = lwc_pd, 
         md = lwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "lwc") %>% 
  select(-lwc_pd, -lwc_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(lwc_pd, lwc_md, water_potential_md, water_potential_pd) %>% 
  select(-lwc_md, -lwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_lwc) %>% 
  distinct() %>% 
 # select(-lwc_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(lwc = mean(lwc, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T), 
            site = site)
```

###nice hyd

#####Tall: 
```{r, echo=FALSE, fig.height= 5, fig.width= 2}
wk_figs <- wk_all_long %>% 
  filter(week %in% c(10, 14, 17, 19, 21, 29, 33, 37), 
         lwc < 6, 
         lwc > 0
         ) %>% 
  mutate(week_nice = case_when(
    week == 10 ~ "Week 10", 
    week == 14 ~ "Week 14", 
    week == 17 ~ "Week 17", 
    week == 19 ~ "Week 19", 
    week == 21 ~ "Week 21", 
    week == 29 ~ "Week 29",
    week == 33 ~ "Week 33",
    week == 37 ~ "Week 37"
  )) 

wk_figs_labels <-
  data.frame(
    label = c('10', '11', '17', '19', '21', '29', '33', '33'),
    week_nice = c(
      "Week 10",
      "Week 14",
      "Week 17",
      "Week 19",
      "Week 21",
      "Week 29",
      "Week 33",
      "Week 37"
    )
  )

nice_hyd <- wk_figs %>% 
  filter(!(week == 29 & lwc > 1)) %>% 
  ggplot(aes(y = -1*water_potential, 
             x = lwc,
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time,
                 color = as.factor(tree)
                 ), 
             size = 2, 
             alpha = .6) + 
  geom_smooth(method = "lm",
              se = F, 
              alpha = .3) +
  facet_wrap(~week_nice, 
             ncol = 1,
              strip.position="top"
            # scales = "free"
             ) +
  #annotate("text", x= .5, y = 6, label =unique(wk_figs$week_nice))+
 # theme(legend.position = "none") +
  theme(
      legend.position="none",
      strip.background = element_blank(),
     # strip.text = element_text(size=9, lineheight=.3),
     # panel.spacing = unit(0, "lines"),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
       axis.title = element_text(size = 16), 
    # panel.margin = unit(c(-0.2,0, -0.2,0), "lines")
    ) +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "Leaf Water Content (g)", 
       #caption = "triangles = predawn, circles = midday"
       ) +
  xlim(.5,2) #+
  #geom_text(aes(label = label), data = wk_figs_labels, x= .5, y = 6) 

nice_hyd

ggsave(here("figures", "nice_hydration"), nice_hyd, device = "jpg", width = 3, height = 9, dpi = 300)
```

#####Layered

```{r, include = F, eval=F}
# df_grey_groups %>% 
#   ggplot() +
#   geom_point(aes(y=water_potential,x= lwc, group = tree, color=color)) + 
#   geom_line(aes(y=water_potential,x= lwc, group = tree, color=color)) + 
#   scale_color_identity(labels = c(blue = "a",gray = "Other"),guide = "legend")

("#c969a1", "#ce4441", "#ee8577", "#eb7926", "#ffbb44", "#859b6c", "#62929a", "#004f63", "#122451")
```


```{r}
df_all_groups <- wk_figs %>% 
  mutate(tree_week = paste(tree, week, sep = "_")
  ) %>% 
  mutate(water_potential = -1*water_potential)
  

df_grey <- df_all_groups

df_1 <- df_all_groups %>% 
  filter(week %in% c('10'))

df_2 <- df_all_groups %>% 
  filter(week %in% c('17'))

df_3 <- df_all_groups %>% 
  filter(week %in% c('21'))

df_4 <- df_all_groups %>% 
  filter(week %in% c('37'))

nice_hydration_layered <- ggplot() +
    geom_point(aes(y = water_potential, x = lwc, shape = time), data = df_grey, color = "grey") +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week), color = "grey", data = df_grey) +
    geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_1"), 
               data = df_1 ) +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_1"), 
              data = df_1) +
    geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_2"), 
               data = df_2) +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_2"), 
              data = df_2) +
    # geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_3"), 
    #            data = df_3) +
    # geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_3"), 
    #           data = df_3) +
    geom_point(aes(y = water_potential, x = lwc, shape = time, color = "df_4"), 
               data = df_4) +
    geom_line(aes(y = water_potential, x = lwc, group = tree_week, color = "df_4"), 
              data = df_4
              ) +
    scale_colour_manual(name = 'Week', 
         values =c("df_1" ="#122451", 
                   "df_2"="#528791",
                  # "df_3"="#EC7E28",
                   "df_4"="#c969a1"
                   ), 
         labels = c('10',
                    '17',
                  #  '21',
                    '33')) +
    labs(y = "Water Potential (MPa)", 
       x = "Leaf Water Content (g)", 
       color= "Week", 
       shape = "Time"
       #caption = "triangles = predawn, circles = midday"
       ) +
  theme(
    legend.position = c(.9, .35),
  #strip.background = element_blank(),
  #strip.text.y = element_blank(), 
  #strip.text.x = element_text(size = 16), 
  axis.text.y = element_text(size = 12), 
  axis.text.x = element_text(size = 12), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 14), 
  legend.title = element_text(size = 14), 
  legend.text = element_text(size = 14), 
# legend.position = "none"
  ) +
   xlim(.5,2) #+
nice_hydration_layered
  
ggsave(here("figures", "nice_hydration_layered"), nice_hydration_layered, device = "jpg", width = 6, height = 4, dpi = 300)
```

```{r, include=F}
wc_lm_hyd_df <- wk_all

for (i in unique(wc_lm_hyd_df$week)) {

  df <- wc_lm_hyd_df %>%
    filter(week == i)

  p <- df %>%
  ggplot(aes(y = water_potential,
             x = lwc,
             color = as.factor(tree)
             )) +
  geom_point(aes(shape = time)) +
  geom_smooth(method = "lm",
              se = F) +
  #theme(legend.position = "none") +
  labs(title = i)

  if (!is.null(p)) plot(p)

}
```

Slopes of the formula: 

```{r, warning=T}
m_wk_rand <- lmer(-1*water_potential ~ lwc + (lwc|tree) + (lwc|week), data = wk_all )
#m_wk_rand
#summary(m_wk_rand)
```

Should we include site? 

```{r, include = F}
wk_all_sites <- wk_all %>% mutate(site = as.factor(site)) %>% 
  drop_na(site)

m_wk_rand_nosite <- lmer(-1*water_potential ~ lwc + (lwc|tree) + (lwc|week), data = wk_all_sites, REML = T)
#m_wk_rand_nosite

m_wk_rand_site <- lmer(-1*water_potential ~ lwc + (lwc|tree) + (lwc|week) + (1|site), data = wk_all_sites, REML = T)
#m_wk_rand_site

anova(m_wk_rand_nosite, m_wk_rand_site)
```

...NO, we do not need to include site. (p > .05)


What is the slope?

```{r, echo=FALSE}
grand_slope <- broom.mixed::tidy(m_wk_rand)
#grand_slope

#ran_list <- ranef(m_wk_rand)

ran_list2 <- coef(m_wk_rand)

ran_df <- as.data.frame(ran_list2[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc`, 
         -lwc) %>%
  select(-`(Intercept)`)

ran_err <- arm::se.ranef(m_wk_rand)

ran_err_df <- as.data.frame(ran_err[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc`)%>% 
  select(-`(Intercept)`, 
         -lwc) %>% 
  tibble::rownames_to_column("week")

week_ranerr <- nrow(ran_err_df)


ran_df_week <- bind_cols(ran_df, ran_err_df) %>% 
  data_frame()
```

Are the slopes significantly different from each other? 

```{r}
ranef(m_wk_rand, condVar=T)

sjPlot::plot_model(m_wk_rand, type = "re", show.p = T)
```


Random slopes of each week: 

####SLOPES
```{r, echo=FALSE}
hyd_slopes <- ran_df_week %>% 
  filter(!week %in% c(9)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Slope") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18), 
 legend.position = "none"
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 14,15, 17, 18, 19, 21, 29, 33, 39)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none") +
  color_grad
hyd_slopes

ggsave(here("figures", "nice_hydration_slopes"), hyd_slopes, device = "jpg", width = 5, height = 2.5, dpi = 300)
```



Random intercepts of each week:


```{r, echo=FALSE}
hyd_ints <- ran_df_week %>% 
  filter(!week %in% c(9)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Intercept") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 16), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18), 
 legend.position = "none"
  ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 14,15, 17, 18, 19, 21, 29, 33, 39))+
  color_grad
hyd_ints

ggsave(here("figures", "nice_hydration_ints"), hyd_ints, device = "jpg", width = 5, height = 2.5, dpi = 300)
```


#**Space

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df <- wk_all_long %>% 
  filter(!week %in% c(9)) %>% 
  filter(lwc > .44) %>% 
  mutate(water_potential = -1*water_potential) %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_lwc = mean(lwc, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(lwc_centered = lwc - mean_lwc)
  # mutate(lwc_centered = scale(lwc,  scale=FALSE)) %>% 
  # filter(lwc_centered < 4)
```



####SPACE - fig: 
```{r, warning = F, echo=FALSE}
#scaled
space_nice <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = lwc_centered, 
            x = lwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(#legend.position="top",
        legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice

ggsave(here("figures", "nice_space"), space_nice, device = "jpg", width = 6, height = 4, dpi = 300)
```


```{r, warning = F, echo=FALSE}
#scaled
space_nice_centered <- wc_wk_centered_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_centered, 
            #x = lwc,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .5, 
            # aes (shape = site)
             ) +
  theme(legend.position="top",
        #legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Leaf Water Content", 
       color = "Week", 
       shape = "Site") +
  color_many_2 +
  #color_week_all +
  guides(color = guide_legend(nrow = 2))
space_nice_centered

ggsave(here("figures", "nice_space_centered"), space_nice_centered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Do we need to include site here? 

Centered LWC:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data = space_df, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwc_centered  + (lwc_centered|week) + (1|tree) + (1|site), data = space_df,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

...NO. 

LWC uncentered:

```{r}
space_df_nosite <- wc_wk_centered_df %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ lwc + (lwc|week) + (1|tree), data = space_df, REML = T)
#summary(space_mod)

space_mod_site <- lmer(water_potential ~ lwc  + (lwc|week) + (1|tree) + (1|site), data = space_df,  REML = T)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```
...Yes? If using LWC not centered. 



Visualize: 

###SLOPES - space

#####Centered
Get slopes from random effects: 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_centered`, 
         -lwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_centered`)%>% 
  select(-`(Intercept)`, 
         -lwc_centered) %>% 
  tibble::rownames_to_column("week")

# weeks_check <- list(unique(space_df$week)) #%>% as_data_frame() 
# weeks_check

# weeks <- data_frame(1:10)
# weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29, 33) 

ran_df_week <- bind_cols(ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()
```

```{r, echo=FALSE}
ran_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```


```{r, echo=FALSE}
ran_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```

#NOT Centered

Get slopes from random effects: 

NOTE: this includes site random effect, which the centered version does not need. 

```{r, echo=FALSE}
space_mod <- lmer(water_potential ~ lwc + (lwc|week) + (1|tree) + (1|site), data =  wc_wk_centered_df, REML = T)

space_mod_df <- broom.mixed::tidy(space_mod)
#space_mod_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_df3 <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc`, 
         -lwc) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)

ran_err_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc`)%>% 
  select(-`(Intercept)`, 
         -lwc) %>% 
  tibble::rownames_to_column("week")

ran_df_week <- bind_cols(ran_df3, ran_err_df) %>% 
  #select(-`1:10`) %>% 
  data_frame()
```

```{r, echo=FALSE}
ran_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```


```{r, echo=FALSE}
ran_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many_2 +
  guides(color = guide_legend(nrow = 2))
```



###Predawn


```{r, warning = F}
wc_wk_centered_pd_df <- wc_qudo_df %>% 
  filter(time == "pd") %>% 
  group_by(week) %>% 
  mutate(mean_lwc = mean(lwc)) %>% 
  ungroup() %>% 
  mutate(lwc_centered = lwc - mean_lwc)
  # mutate(lwc_centered = scale(lwc,  scale=FALSE)) %>% 
  # filter(lwc_centered < 4)

#not scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  #filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) 
#scaled
wc_wk_centered_pd_df %>% 
  drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
             x = lwc_centered, 
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(alpha = .3, 
             aes (shape = site)) +
  geom_smooth(method = "lm", se = F) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Predawn MPa", 
       x = "LWC (centered by week)", 
       color = "Week", 
       shape = "Site") +
  color_many
```

```{r}
space_pd_df <- wc_wk_centered_pd_df %>% 
  drop_na(site)

space_mod_site <- lmer(water_potential ~ lwc_centered + (lwc_centered|week) + (1|tree), data = space_pd_df, REML = F)
#summary(space_mod)

space_mod <- lmer(water_potential ~ lwc_centered  + (lwc_centered|week) + (1|tree) + (1|site), data = space_pd_df,  REML = F)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```

Get slopes from random effects: 

```{r, echo=FALSE}
space_mod_pd_df <- broom.mixed::tidy(space_mod)
#space_mod_pd_df

ran_list3 <- coef(space_mod)

#ran_list2 <- coef(m_wk_rand)

ran_pd_df <- as.data.frame(ran_list3[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `lwc_centered`, 
         -lwc_centered) %>%
  select(-`(Intercept)`)

ran_err3 <- arm::se.ranef(space_mod)
ran_err_pd_df <- as.data.frame(ran_err3[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `lwc_centered`)%>% 
  select(-`(Intercept)`, 
         -lwc_centered)

weeks_check <- unique(space_pd_df$week) %>% as_data_frame() 

#weeks <- data_frame(1:9)
#weeks$week <- c(9, 10, 11, 12, 14, 15, 17, 21, 29) 

weeks <- tibble(1:8)
weeks$week <- c(10, 14, 15, 17, 19, 21, 29, 33) 

ran_pd_df_week <- bind_cols(weeks, ran_pd_df, ran_err_pd_df) %>% 
 # select(-`1:9`) %>% 
  data_frame()
```


####SLOPES

Visualize: 

```{r, echo=FALSE}
ran_pd_df_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = slope + (std.error.slope/2), 
         lwr = slope - (std.error.slope/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```


```{r, echo=FALSE}
ran_pd_df_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```

#**Time

```{r}
wc_qudo_df %>% 
  filter(!week %in% c(9, 18, 19)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = lwc, 
             x = as.factor(week), 
             #x = date,
            # color = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "LWC", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE, warning = F}
time <- wc_qudo_df %>% 
  drop_na(week) %>% 
 # filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(#aes(size = week), 
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Midday MPa") +
  color_two +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
  facet_wrap(~time, nrow = 2)
time 

ggsave(here("figures", "nice_time"), time, device = "jpg", width = 4, height = 2, dpi = 300)
```



```{r, echo=FALSE}
wc_qudo_df %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = lwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "LWC", 
       y = "Predawn MPa") +
  color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

All dates: 

```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md")
  
time_mod <- lmer(water_potential ~ lwc + (1|week) + (lwc|tree), data = wc_qudo_md_df)
summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
        # slope = `lwc`
         ) %>%
  select(-`(Intercept)`, 
          -lwc)
tree_eff

ran_err_tree <- arm::se.ranef(time_mod)
ran_err_tree <- as.data.frame(ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
        # std.error.slope = `lwc`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree <- bind_cols(tree_eff, ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()

ran_df_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ LWC)") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 
```

Just linear: 
```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "after leafout")
  
  
time_mod <- lmer(water_potential ~ lwc + (1|week) + (lwc|tree), data = wc_qudo_md_df)
summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
        # slope = `lwc`
         ) %>%
  select(-`(Intercept)`, 
          -lwc)
tree_eff

ran_err_tree <- arm::se.ranef(time_mod)
ran_err_tree <- as.data.frame(ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
        # std.error.slope = `lwc`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree_after <- bind_cols(tree_eff, ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame() %>% 
  mutate(time_season = "After Leafout")

ran_df_tree_after %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 
```
Before leafout: 
```{r}
wc_qudo_md_df <- wc_qudo_df %>% 
  filter(time == "md") %>% 
  filter(time_season == "before leafout")
  
  
time_mod <- lmer(water_potential ~ lwc + (1|week) + (lwc|tree), data = wc_qudo_md_df)
summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
        # slope = `lwc`
         ) %>%
  select(-`(Intercept)`, 
          -lwc)
tree_eff

ran_err_tree <- arm::se.ranef(time_mod)
ran_err_tree <- as.data.frame(ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
        # std.error.slope = `lwc`
         )%>% 
  select(-`(Intercept)`, 
        # -lwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_tree_before <- bind_cols(tree_eff, ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()%>% 
  mutate(time_season = "Before Leafout")

ran_df_tree_before %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "lwc") %>% 
  mutate(upr = estimate + (std.error/2), 
         lwr = estimate - (std.error/2)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, BEFORE LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 
```

####SLOPES - combined

```{r}
ran_df_tree_before_vs_after <- bind_rows(ran_df_tree_before, ran_df_tree_after)

ef <- ran_df_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate( sd = sd(estimate),
    estimate = mean(estimate), 
        # std.error = mean(std.error),
         upr = estimate + sd, 
         lwr = estimate - sd, 
         time_season = as.factor(time_season)) %>% 
  select(estimate, upr, lwr, time_season, sd)

time_summary <- ef %>% 
ggplot() + 
  geom_point(aes(y = estimate, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
                 for each time frame", 
       x = "Time")
time_summary

ggsave(here("figures", "time_summary_slopes"), time_summary, device = "jpg", width = 2.5, height = 3, dpi = 300)
```


```{r}
ran_df_tree_before_vs_after <- bind_rows(ran_df_tree_before, ran_df_tree_after)

ef <- ran_df_tree_before_vs_after %>% 
 # group_by(time_season) %>% 
  mutate( sd = sd(estimate),
    estimate = mean(estimate), 
        # std.error = mean(std.error),
         upr = estimate + sd, 
         lwr = estimate - sd, 
         time_season = as.factor(time_season)) %>% 
  select(estimate, upr, lwr, time_season, sd)

time_summary_all <- ef %>% 
ggplot() + 
  geom_point(aes(y = estimate, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
                 for each time frame", 
       x = "Time")
time_summary_all

ggsave(here("figures", "time_summary_slopes"), time_summary_all, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

Predawn slopes for each individual: 

```{r, echo=FALSE}
wc_qudo_pd_df <- wc_qudo_df %>% 
  filter(time == "pd")

time_mod <- lmer(water_potential ~ lwc + (lwc|week) + (1|tree), data = wc_qudo_pd_df)
summary(time_mod)
```


