---
title: "Establishing relationships between cwc and MPa, Part 2"
author: "Indra Boving"
date: "11/9022"
output:
  html_document: default
  word_document: default
---

#Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
#install.packages("")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)
library(vars)
library(MuMIn)
library(lme4) #for mixed effects models
library(arm)
library(nlme)
select = dplyr::select

source(here::here("scripts", "scripts_functions", "figure_info.R"))

#datver <- "01052023"
dataversion <- paste0("Data_", datver)
```

#Data wrangling: 
```{r}
datver_cwc <- "05042022" #Just change this in the 1_combined_processing.Rmd
dataversion_cwc <- paste0("Data_", datver_cwc)

cwc_raw <- read_csv(here(dataversion_cwc,"cwc-alldates.csv"), show_col_types = F) %>% 
  clean_names() %>% 
  mutate(tree = la_tree_id) %>% 
  pivot_longer(cols = (6:17),
              names_to = "date", 
               values_to = "cwc") %>% 
  mutate(date = gsub("x", "", date, fixed = TRUE), 
         date = ymd(date), 
         week = week(date), 
         tree = as.character(tree)) %>% 
  group_by(tree, week) %>% 
  mutate(cwc = mean(cwc)) %>% 
  rename(week_cwc_link = week)

unique(cwc_raw$week_cwc_link)
unique(cwc_lwc_raw$week)

cwc_lwc_raw <- read_csv(here("processed-data", paste0("lfm_rwc_alas_wp_wc_df",datver,".csv")), show_col_types = F) %>% 
  filter(type == "leaf",
        # !week == 9, 
        # time == 'md'
        ) %>% 
  mutate(time_season = case_when(
    week <= 17 ~ "before leafout", 
    week > 17 ~ "after leafout", 
    TRUE ~ as.character("none")
  )) %>% 
  mutate(water_potential = -1*mpa_mean) %>% 
  rename(date_alas = date) %>% 
  select(-X, -'...1') %>% 
  mutate(week_cwc_link = case_when( #so that the weeks of overlights overlap with the weeks of sample collection
    week %in% c(8, 9) ~ 9, 
    week %in% c(14, 13) ~ 14, 
    week %in% c(17) ~ 16, 
    week %in% c(21) ~ 20,
    TRUE ~ as.numeric(week)
  )) %>% 
  filter(week_cwc_link < 22)

#Combine: 
unique(cwc_raw$week_cwc_link) #cwc weeks
unique(cwc_raw$date) #cwc weeks
unique(cwc_lwc_raw$week_cwc_link) #other physiology weeks
unique(cwc_lwc_raw$date_wp)

unique(cwc_raw$tree)
unique(cwc_lwc_df$tree)

cwc_lwc_all_df <- merge(cwc_raw, cwc_lwc_raw, by = c("tree", "week_cwc_link"), all = T) %>% 
  distinct() %>% 
  filter(cwc > -100) %>% 
  drop_na(site, species) %>% 
 # select(-x1, -"...1") %>% 
  group_by(tree, time, week) %>% 
  mutate(alas_cm2_per_mm2 = case_when(
    alas_cm2_per_mm2 > 20 ~ NA_real_, 
    TRUE ~ as.numeric(alas_cm2_per_mm2)
  )) %>% 
  mutate(alas_mean = mean(alas_cm2_per_mm2, na.rm = T),
         sla_mean = mean(sla_cm_g,na.rm = T), 
         lma_mean = mean(lma_g_cm2,na.rm = T),
         lwa_mean = mean(lwa_g_cm2,na.rm = T),
         leaf_count_mean = mean(leaf_count, na.rm = T),
         leaf_area_mean = mean(area_cm2, na.rm = T), 
         ldmc_mean = mean(ldmc, na.rm = T),
         date_shift = date) %>% 
  # select(tree, shift_id, species, week, lat, lon, time, type, date_shift, date_rwc, date_alas, date_wp, cwc, mpa_mean, lwc_mean, mean_swc_per_dry_g, mean_swc_g, rwc_lfm_percent, rwc_lwc_percent, lfm_percent, alas_mean, sla_mean, lma_mean, lwa_mean, leaf_count_mean, leaf_area_mean) %>% 
   distinct() %>% 
  drop_na(time) %>% 
  ungroup() %>% 
  group_by(tree, week, time, type) %>% 
  mutate(rwc_percent = case_when(
    rwc_lfm_percent == NA ~ mean(c(rwc_lfm_percent, rwc_lwc_percent, na.rm = T)),
    rwc_lwc_percent == NA ~ mean(c(rwc_lfm_percent, rwc_lwc_percent, na.rm = T)),
    rwc_lfm_percent > 0 ~ mean(c(rwc_lfm_percent, rwc_lwc_percent, na.rm = T)), 
    TRUE~ as.numeric(rwc_lwc_percent)
  ))

cwc_df_cwc <-  cwc_lwc_all_df %>% 
  select(tree, shift_id, species, week, lat, lon, time, type, date_shift, date_rwc, date_alas, date_wp, cwc, mpa_mean, lwc_mean, mean_swc_per_dry_g, mean_swc_g, rwc_lfm_percent, rwc_lwc_percent, lfm_percent, alas_mean, sla_mean, lma_mean, lwa_mean, leaf_count_mean, leaf_area_mean, week_cwc_link, water_potential) %>%
   distinct() %>% 
  drop_na(time) 
```



What is the linear portion? 


Week 17 looks like a good cutoff:
```{r, echo=F}
wc_lm_df_cwc <- cwc_df_cwc %>% 
  filter(week > 17)
```

From what weeks do we have the most trees?
```{r, echo=F}
cwc_df_cwc %>% 
  select(week, time, tree, cwc) %>% 
  drop_na(cwc) %>% 
  unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") + 
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "cwc counts") +
  color_fill
```

```{r, echo=F}
cwc_df_cwc %>% 
    select(week, time, tree, water_potential) %>% 
  drop_na(water_potential) %>% 
 # unique() %>% 
  group_by(week, time) %>% 
  count() %>% 
  ggplot(aes(x = week, y = n, fill = time)) +
  geom_col(stat = "identity") +
  scale_x_continuous(breaks = seq(9, 40, by = 1))+
  labs(y = "MPa counts") +
  color_fill
```
A: week 17, 21, 29, 10

#Timeline

```{r, fig.height=.75, fig.width=6}
cwc_df_cwc %>% 
  filter(time == "md", 
         week < 38,
        # !week %in% c(18)
         ) %>% 
  #ggplot(aes(x = week, y = 0, color = mean(water_potential, na.rm = T)))+
  ggplot(aes(x = week, y = 0, color = as.character(week)))+
  geom_hline(yintercept = 0) +
  geom_point(size = 5) +
  color_week_assigned +
  ylim(-.25, +.25)  + 
  scale_x_continuous(breaks = c(9, 10, 11, 12, 13, 14,15, 16, 17, 18, 19, 20, 21)
                      # seq(10, 30, by = 1)
                     ) +
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        )
```
```{r, fig.height=1, fig.width=12}
timeline_df_cwc <- cwc_df_cwc %>% 
 # select(week, date_wp, time) %>% 
  mutate(date_wp = as.character(date_wp)) %>% 
  mutate(date_new = case_when(
    date_wp %in% c("2022-03-23") ~ "2022-03-25",
    date_wp %in% c("2022-03-30","2022-04-06") ~ "2022-04-04",
    date_wp %in% c("2022-04-13") ~ "2022-04-11",
    date_wp %in% c("2022-04-27") ~ "2022-04-25",
    date_wp %in% c("2022-05-04") ~ "2022-05-09",
    date_wp %in% c("2022-05-23") ~ "2022-05-25",
    TRUE ~ as.character(date_wp)
  )) %>% 
  mutate(date_new = ymd(date_new)) %>% 
  select(date_new, week) %>% 
  distinct()


timeline_plot <- timeline_df_cwc %>% 
 # filter(time == "md") %>% 
  ggplot(aes(x = date_new, y = 0, color = as.character(week)))+
  geom_hline(yintercept = 0) +
  geom_point(size = 10) +
  color_week_assigned +
  ylim(-.25, +.25)  + 
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.title.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(), 
        axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=.5, size= 20)
        ) +
scale_x_date(date_labels = '%b. %d',
             breaks = as.Date(c("2022-03-08","2022-03-15", "2022-03-25", 
                                #"2022-03-23", "2022-03-30", 
                                "2022-04-04", #"2022-04-06","2022-04-13", 
                                "2022-04-11", #"2022-04-27", 
                                "2022-04-25", #"2022-05-04" ,
                                "2022-05-09", "2022-05-25", 
                                #"2022-05-23", 
                                "2022-07-19", "2022-08-18","2022-09-15")))
timeline_plot

ggsave(here("figures", "timeline_plot_cwc"), timeline_plot, device = "jpg", width = 12, height = 2, dpi = 300)
```

#View: 

```{r, echo=FALSE}
cwc_df_cwc %>% 
  #filter(week %in% c(10, 13, 17, 21, 29)) %>% 
  filter(cwc < 5) %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = as.factor(tree),
             shape = time
             )) +
  geom_point(aes(shape = time)) + 
  geom_smooth(method = "lm",
              se = F) +
  facet_wrap(~week_cwc_link, scales = "free") +
 # theme(legend.position = "none") +
  color_very_many +
  labs(y = "Water Potential (MPa)", 
       x = "cwc")
```

```{r, warning = F}
wk_all <- cwc_df_cwc 

wk_all_wide <- wk_all %>% 
  drop_na(date_wp) %>% 
  pivot_wider(names_from=time, 
              values_from = c(cwc, water_potential)) %>% 
    dplyr::group_by(tree, week) %>%
  fill(c(cwc_md, cwc_pd, water_potential_pd, water_potential_md), .direction = "downup") %>%
  dplyr::ungroup()%>% 
  select(-date_wp) %>% 
  distinct()

wk_all_long_cwc <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-water_potential_md, -water_potential_pd) %>% 
  mutate(pd = cwc_pd, 
         md = cwc_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "cwc") %>% 
  select(-cwc_pd, -cwc_md)

wk_all_long_mpa <- wk_all_wide %>% 
  drop_na(cwc_pd, cwc_md, water_potential_md, water_potential_pd) %>% 
  select(-cwc_md, -cwc_pd) %>% 
  mutate(pd = water_potential_pd, 
         md = water_potential_md) %>% 
  pivot_longer(cols = c(pd, md), 
               names_to = "time", 
               values_to = "water_potential") %>% 
  select(-water_potential_pd, -water_potential_md)

wk_all_long <- merge(wk_all_long_mpa, wk_all_long_cwc) %>% 
  distinct() %>% 
 # select(-cwc_NA, -water_potential_NA) %>% 
  group_by(tree, week, time) %>% 
  summarise(cwc = mean(cwc, na.rm = T), 
            water_potential = mean(water_potential, na.rm = T))
```


#####****Layered

```{r, include = F, eval=F}
# df_grey_groups %>% 
#   ggplot() +
#   geom_point(aes(y=water_potential,x= cwc, group = tree, color=color)) + 
#   geom_line(aes(y=water_potential,x= cwc, group = tree, color=color)) + 
#   scale_color_identity(labels = c(blue = "a",gray = "Other"),guide = "legend")

("#c969a1", "#ce4441", "#ee8577", "#eb7926", "#ffbb44", "#859b6c", "#62929a", "#004f63", "#122451")
```


```{r}
df_all_groups <- wk_all_long  %>% 
  mutate(tree_week = paste(tree, week, sep = "_")
  ) %>% 
  mutate(water_potential = water_potential)
  

df_grey <- df_all_groups

df_1 <- df_all_groups %>% 
  filter(week %in% c('10'))

df_2 <- df_all_groups %>% 
  filter(week %in% c('17'))

df_3 <- df_all_groups %>% 
  filter(week %in% c('21'))

df_4 <- df_all_groups %>% 
  filter(week %in% c('37'))

nice_hydration_layered <- ggplot() +
    geom_point(aes(y = water_potential, x = cwc, shape = time), data = df_grey, color = "grey") +
    geom_line(aes(y = water_potential, x = cwc, group = tree_week), color = "grey", data = df_grey) +
    geom_point(aes(y = water_potential, x = cwc, shape = time, color = "df_1"), 
               data = df_1 ) +
    geom_line(aes(y = water_potential, x = cwc, group = tree_week, color = "df_1"), 
              data = df_1) +
    geom_point(aes(y = water_potential, x = cwc, shape = time, color = "df_2"), 
               data = df_2) +
    geom_line(aes(y = water_potential, x = cwc, group = tree_week, color = "df_2"), 
              data = df_2) +
    # geom_point(aes(y = water_potential, x = cwc, shape = time, color = "df_3"), 
    #            data = df_3) +
    # geom_line(aes(y = water_potential, x = cwc, group = tree_week, color = "df_3"), 
    #           data = df_3) +
    geom_point(aes(y = water_potential, x = cwc, shape = time, color = "df_4"), 
               data = df_4) +
    geom_line(aes(y = water_potential, x = cwc, group = tree_week, color = "df_4"), 
              data = df_4
              ) +
    scale_colour_manual(name = 'Week', 
         values =c("df_1" ="#122451", 
                   "df_2"="#62929a",
                  # "df_3"="#EC7E28",
                   "df_4"="#c969a8"
                   ), 
         labels = c('10',
                    '17',
                  #  '21',
                    '33')) +
    labs(y = "Water Potential (MPa)", 
       x = "Leaf Water Content (g)", 
       color= "Week", 
       shape = "Time"
       #caption = "triangles = predawn, circles = midday"
       ) +
  theme(
    #legend.position = c(.9, .35),
   # legend.position = "none",
     legend.position = "right",
  #strip.background = element_blank(),
  #strip.text.y = element_blank(), 
  #strip.text.x = element_text(size = 16), 
  axis.text.y = element_text(size = 12), 
  axis.text.x = element_text(size = 12), 
  #axis.ticks.y = element_blank(), 
  axis.title.y = element_text(size = 20), 
  axis.title.x = element_text(size = 20), 
 # axis.title.x = element_blank(),
  legend.title = element_text(size = 14), 
  legend.text = element_text(size = 14), 
# legend.position = "none"
  ) +
   xlim(.5,2) +
  scale_x_reverse()
nice_hydration_layered
  
ggsave(here("figures", "nice_hydration_layered_cwc"), nice_hydration_layered, device = "jpg", width = 6, height = 4, dpi = 300)
```

Slopes of the formula: 

```{r, warning=T}
m_wk_rand <- lmer(water_potential ~ cwc + (cwc|tree) + (cwc|week), data = wk_all )
```


#**Space

1. Center and scale by week
2. Plot all midday grand slopes

###Midday: 

```{r, warning = F}
wc_wk_centered_df_cwc <- wk_all_long %>% 
  #filter(!week %in% c(9)) %>% 
  mutate(water_potential = water_potential) %>% 
  filter(time == "md") %>% 
  group_by(week) %>% 
  mutate(mean_cwc = mean(cwc, na.rm = T)) %>% 
  ungroup() %>% 
  mutate(cwc_centered = cwc - mean_cwc)
  # mutate(cwc_centered = scale(cwc,  scale=FALSE)) %>% 
  # filter(cwc_centered < 4)

#scaled
space_nice <- wc_wk_centered_df_cwc %>% 
  #drop_na(site) %>% 
  ggplot(aes(y = water_potential, 
            # x = cwc_centered, 
            x = cwc_centered,
             #color = tree_factor
             color = as.factor(week)
             )) +
  geom_point(#alpha = .5, 
            # aes (shape = site)
             ) +
  theme(#legend.position="none",
        legend.position="top",
       # legend.position= c(.7, .2),
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
     # axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
      axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Centered Canopy Water Content", 
       color = "Week") +
  color_week_assigned +
  #color_week_all +
  guides(color = guide_legend(nrow = 1))
space_nice

wc_wk_centered_df_cwc$week

ggsave(here("figures", "nice_space_cwc"), space_nice, device = "jpg", width = 6, height = 4, dpi = 300)
```

###SLOPES - space


##Covatiation bw LMA, MPa, SWC, LWA

#####Centered
Get slopes from random effects: 

```{r, echo=FALSE}
space_mod_cwc <- lmer(water_potential ~ cwc_centered + (cwc_centered|week) + (1|tree), data =  wc_wk_centered_df_cwc, REML = T)

space_mod_df_cwc_cwc <- broom.mixed::tidy(space_mod_cwc)
#space_mod_df_cwc

ran_list3_cwc <- coef(space_mod_cwc)

#ran_list2 <- coef(m_wk_rand)

ran_df_cwc3_cwc <- as.data.frame(ran_list3_cwc[['week']])%>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc_centered`, 
         -cwc_centered) %>%
  select(-`(Intercept)`)

ran_err3_cwc <- arm::se.ranef(space_mod_cwc)

ran_err_df_cwc_cwc <- as.data.frame(ran_err3_cwc[['week']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc_centered`)%>% 
  select(-`(Intercept)`, 
         -cwc_centered) %>% 
  tibble::rownames_to_column("week") %>% 
  mutate(week = as.numeric(week))

# weeks_check <- list(unique(space_df_cwc$week)) #%>% as_data_frame() 
# weeks_check

# weeks <- data_frame(1:10)
# weeks$week <- c(9, 10, 14, 15, 17, 18, 19, 21, 29, 33) 

ran_df_cwc_week_3_cwc <- bind_cols(ran_df_cwc3_cwc, ran_err_df_cwc_cwc) %>% 
  #select(-`1:10`) %>% 
  data_frame()

ran_df_cwc_week_3_cwc %>% 
 # mutate(week = as.factor(week)) %>% 
  mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= as.character(week))
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = as.character(week)))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope") +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(9, 10, 11, 12, 14,15, 16, 18, 19, 20, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
  color_week_assigned +
   # color_many_2 +
  guides(color = guide_legend(nrow = 1))
```

Intercepts - centered

```{r, echo=FALSE}
ran_df_cwc_week_3 %>% 
   mutate(week = as.numeric(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept") +
  theme(legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
  scale_x_continuous(breaks = c(10, 12, 14,15, 17, 19, 21, 29, 33, 37)
                      # seq(10, 30, by = 1)
                     ) +
    color_grad +
  guides(color = guide_legend(nrow = 2))
```




####SLOPES

Visualize: 

```{r, echo=FALSE}
ran_pd_df_cwc_week %>% 
  mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = slope ,x = week), size =2) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "Week", 
       y = "Slope")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
      axis.title.x = element_blank(),
  axis.title.y = element_text(size = 20), 
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```


```{r, echo=FALSE}
ran_pd_df_cwc_week %>% 
   mutate(week = as.factor(week)) %>% 
 # filter(week %in% c(14, 15, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= week)
    ) + 
  geom_point(aes(y = estimate,x = week), size =3) +
    geom_point(aes(y = upr, x = week), size = 1) +
  geom_point(aes(y = lwr, x = week), size = 1) +
  #geom_line(aes(group = week, y = week, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = week, 
                   xend = week, 
                   color = week))+
  labs(x = "Week", 
       color = "week", 
       y = "Intercept")  +
  theme(legend.position="top",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_hline(yintercept = 0, linetype="dotted") + 
    color_many +
  guides(color = guide_legend(nrow = 1))
```

#**Time

```{r}
cwc_df_cwc %>% 
  #filter(!week %in% c(9, 18, 19)) %>% 
  drop_na(week) %>% 
  ggplot(aes(y = cwc, 
             x = as.factor(week), 
             #x = date,
            # color = as.factor(week), 
             fill = time)) +
  geom_boxplot() +
 # facet_wrap(~time) +
  color_many +
  color_fill +
  labs(y = "cwc", 
       x = "Week", 
       fill = "Time")
```

```{r, echo=FALSE, warning = F}
time_cwc_df_cwc <- cwc_df_cwc %>% 
  mutate(time_season = case_when(
    week < 17 ~ "Before Leafout", 
    week >= 18 ~ "After Leafout", 
    TRUE ~ as.character(week)
  ))

time <- time_cwc_df_cwc %>% 
  drop_na(week) %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = time_season, 
             size = week,
             shape = as.factor(tree),
             show.legend = FALSE)) +
  geom_point(size = 1,
             alpha = .3)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "cwc", 
       y = "Midday MPa") +
  #color_two_grey +
  theme(
      legend.position="none",
      strip.background = element_blank(),
      strip.text.x = element_text(size = 12),
      plot.title = element_text(size=13),
      axis.title = element_text(size = 16),
     axis.text = element_text(size = 12),
     legend.key=element_blank(), 
     legend.text = element_text(size = 13), 
     legend.title = element_text(size = 16),
     legend.margin=margin(0,0,0,0),
      legend.box.margin=margin(-5,-8,-8,-8)
    ) +
  geom_smooth(method = "lm", se = F) + 
 # geom_vline(xintercept = 0, linetype = "dotted") +
  labs(y= "Middays (MPa)", 
       x = "Leaf Water Content (g)", 
       color = "Week", 
       ) +
  guides(color = guide_legend(nrow = 2)) +
 # facet_wrap(~time, nrow = 2) +
  color_two_grey
time_cwc 

ggsave(here("figures", "nice_time_cwc"), time_cwc, device = "jpg", width = 4, height = 2, dpi = 300)
```

```{r, echo=FALSE}
cwc_df_cwc %>% 
  filter(time == "md") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(#aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "Canopy Water Content", 
       y = "Midday MPa") +
  color_very_many +
  theme(legend.position = "none")
```

```{r, echo=FALSE}
cwc_df_cwc %>% 
  filter(time == "pd") %>% 
  ggplot(aes(y = water_potential, 
             x = cwc, 
             color = as.factor(tree), 
             show.legend = FALSE)) +
  geom_point(#aes(size = week), 
             alpha = .2)+
  geom_smooth(method = "lm", se = F) +
 # theme(legend.position = "none") +
  labs(x = "Canopy Water Content", 
       y = "Predawn MPa") +
  color_very_many +
  theme(legend.position = "none")
```
Midday slopes for each individual: 

All dates: 

# Include site?

```{r}
space_df_cwc_nosite <- cwc_df_cwc %>% 
  drop_na(site)

space_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree), data = space_df_cwc_nosite, REML = F)
#summary(space_mod)
AIC(space_mod)

space_mod_site <- lmer(water_potential ~ cwc  + (1|week) + (cwc|tree) + (1|site), data = space_df_cwc_nosite,  REML = F)

AIC(space_mod_site)
#summary(space_mod_site)

anova(space_mod, space_mod_site)
```


```{r}
wc_qudo_md_df_cwc <- cwc_df_cwc %>% 
  filter(time == "md")
  
time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = wc_qudo_md_df_cwc)
#time_mod <- lmer(water_potential ~ cwc + (cwc|tree), data = wc_qudo_md_df_cwc)

summary(time_mod)

ran_list <- coef(time_mod)

tree_eff <- as.data.frame(ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = cwc
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
tree_eff

ran_err_tree1 <- arm::se.ranef(time_mod)

ran_err_tree2 <- as.data.frame(ran_err_tree1[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

ran_df_cwc_tree <- bind_cols(tree_eff, ran_err_tree2) %>% 
  #select(-`1:47`) %>% 
  data_frame()

ran_df_cwc_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

ran_df_cwc_tree %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()

ran_df_cwc_tree %>% 
  mutate(tree = as.factor(tree)) %>% 
  mutate(upr = slope + (std.error), 
         lwr = slope - (std.error)) %>% 
  ggplot(aes(color= estimate)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = estimate))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope (Midday MPa ~ cwc)") +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
  theme(legend.position = "none", 
        axis.text.x = element_blank())#+
  #theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

Just linear: 
```{r}
lin_wc_qudo_md_df_cwc <- time_cwc_df_cwc %>% 
  filter(time == "md") %>% 
  filter(week > 17) %>% 
  drop_na(site)
  
  
lin_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = lin_wc_qudo_md_df_cwc)
summary(lin_time_mod)

lin_ran_list <- coef(lin_time_mod)
lin_ran_list

lin_tree_eff <- as.data.frame(lin_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`,
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
lin_tree_eff

lin_ran_err_tree <- arm::se.ranef(lin_time_mod)

lin_ran_err_tree <- as.data.frame(lin_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
        # -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

lin_ran_df_cwc_tree_after <- bind_cols(lin_tree_eff, lin_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame() %>% 
  mutate(time_season = "After Leafout")

#With standard errors around estimates:

#intercetps 
lin_ran_df_cwc_tree_after%>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = estimate + (std.error), 
         lwr = estimate - (std.error)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = estimate ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Intercepts, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 


ran_df_cwc_tree_after %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, AFTER LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

ran_df_cwc_tree_after %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```
Before leafout: 

```{r}
bef_wc_qudo_md_df_cwc <- cwc_df_cwc %>% 
  filter(time == "md") %>% 
  filter(week < 17) %>% 
  drop_na(site)
  
  
bef_time_mod <- lmer(water_potential ~ cwc + (1|week) + (cwc|tree) + (1|site), data = bef_wc_qudo_md_df_cwc, REML = T)
summary(bef_time_mod)

bef_ran_list <- coef(bef_time_mod)

bef_tree_eff <- as.data.frame(bef_ran_list[['tree']]) %>% 
  mutate(estimate = `(Intercept)`, 
         slope = `cwc`, 
         sd = sd(slope)
         ) %>%
  select(-`(Intercept)`, 
          -cwc)
bef_tree_eff

bef_ran_err_tree <- arm::se.ranef(bef_time_mod)

bef_ran_err_tree <- as.data.frame(bef_ran_err_tree[['tree']]) %>% 
  mutate(std.error = `(Intercept)`, 
         std.error.slope = `cwc`
         )%>% 
  select(-`(Intercept)`, 
         -cwc
         ) %>% 
  tibble::rownames_to_column("tree") # Apply rownames_to_column

bef_ran_df_cwc_tree_before <- bind_cols(bef_tree_eff, bef_ran_err_tree) %>% 
  #select(-`1:47`) %>% 
  data_frame()%>% 
  mutate(time_season = "Before Leafout")

bef_ran_df_cwc_tree_before %>% 
  mutate(tree = as.factor(tree)) %>% 
 # filter(tree %in% c(14, 17, 21, 29)) %>% 
 # filter(term == "cwc") %>% 
  mutate(upr = slope + (std.error.slope), 
         lwr = slope - (std.error.slope)) %>% 
  ggplot(aes(color= tree)
    ) + 
  geom_point(aes(y = slope ,x = tree), size =3) +
    geom_point(aes(y = upr, x = tree), size = 1) +
  geom_point(aes(y = lwr, x = tree), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = tree, 
                   xend = tree, 
                   color = tree))+
  labs(x = "Tree", 
       color = "Tree", 
       y = "Slope, BEFORE LEAFOUT") +
   # facet_wrap(~y_var_name, scales = "free") + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank(), 
  strip.text.x = element_text(size = 18), 
 # axis.text.y = element_blank(), 
  #axis.ticks.y = element_blank(), 
  axis.title = element_text(size = 20), 
  legend.title = element_text(size = 18)
  ) +
 # geom_hline(yintercept = 0, linetype="dotted") + 
 # scale_x_continuous(breaks = seq(9, 30, by = 1)) +
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  color_very_many 

ran_df_cwc_tree_before %>% 
  ggplot(aes(x = slope))+
  #geom_histogram() +
  geom_density()
```

####SLOPES - combined

```{r}
ran_df_cwc_tree_before_vs_after <- bind_rows(bef_ran_df_cwc_tree_before, lin_ran_df_cwc_tree_after)

ef <- ran_df_cwc_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate(sd = sd(slope),
         slope = mean(slope), 
         mean_se = mean(std.error.slope),
        mean_std.error = mean(std.error),
        upr_sd = slope + mean_std.error,
        lwr_sd = slope - mean_std.error,
         upr = slope + mean_se,
         lwr = slope - mean_se,
         time_season = as.factor(time_season)) 
# %>% 
#   select(slope, upr, lwr, time_season, sd)

time_summary <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SE acrss all trees
            for each time frame", 
       x = "Time")
time_summary

time_summary_sd <- ef %>% 
ggplot() + 
  geom_point(aes(y = slope, x = time_season), size =3) +
    geom_point(aes(y = upr_sd, x = time_season), size = 1) +
  geom_point(aes(y = lwr_sd, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr_sd, 
                   yend = upr_sd, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
            for each time frame", 
       x = "Time")
time_summary_sd

ggsave(here("figures", "time_summary_slopes"), time_summary, device = "jpg", width = 2.5, height = 3, dpi = 300)
```


```{r}
ran_df_cwc_tree_before_vs_after <- bind_rows(ran_df_cwc_tree_before, ran_df_cwc_tree_after)

ef <- ran_df_cwc_tree_before_vs_after %>% 
  group_by(time_season) %>% 
  mutate(sd = sd(estimate),
    estimate = mean(estimate), 
        # std.error = mean(std.error),
         upr = estimate + sd, 
         lwr = estimate - sd, 
         time_season = as.factor(time_season)) %>% 
  select(estimate, upr, lwr, time_season, sd)

time_summary_all <- ef %>% 
ggplot() + 
  geom_point(aes(y = estimate, x = time_season), size =3) +
    geom_point(aes(y = upr, x = time_season), size = 1) +
  geom_point(aes(y = lwr, x = time_season), size = 1) +
  #geom_line(aes(group = tree, y = tree, x = upr)) +
  geom_segment(aes(y= lwr, 
                   yend = upr, 
                   x = time_season, 
                   xend = time_season)) +
  labs(y = "Mean Slope +/- SD acrss all trees
                 for each time frame", 
       x = "Time")
time_summary_all

ggsave(here("figures", "time_summary_slopes"), time_summary_all, device = "jpg", width = 2.5, height = 3, dpi = 300)
```

Predawn slopes for each individual: 

```{r, echo=FALSE}
wc_qudo_pd_df_cwc <- cwc_df_cwc %>% 
  filter(time == "pd")

time_mod <- lmer(water_potential ~ cwc + (cwc|week) + (1|tree), data = wc_qudo_pd_df_cwc)
summary(time_mod)
```



