

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)

library(tidyverse)
library(sf)
library(raster)
library(leaflet)
library(spdplyr)
library(rgdal)
library(leafsync)
```

```{r}
save_tags <- function (tags, file, selfcontained = F, libdir = "./lib") 
{
  if (is.null(libdir)) {
    libdir <- paste(tools::file_path_sans_ext(basename(file)), 
                    "_files", sep = "")
  }
  htmltools::save_html(tags, file = file, libdir = libdir)
  if (selfcontained) {
    if (!htmlwidgets:::pandoc_available()) {
      stop("Saving a widget with selfcontained = TRUE requires pandoc. For details see:\n", 
           "https://github.com/rstudio/rmarkdown/blob/master/PANDOC.md")
    }
    htmlwidgets:::pandoc_self_contained_html(file, file)
    unlink(libdir, recursive = TRUE)
  }
  return(file)
}
```


## Loading in vector data and reprojecting it with sf package

Sedgwick files from Open Topography -- too big to put all on GitHub, so will need to figure that out later if we actually want to use them. 

```{r}
# sedg_hillshade1 <- raster(here("data", "geospatial", "viz", "viz.be_hillshade-color.tif"))
# plot(sedg_hillshade1)

# sedg_hillshade2 <- raster(here("data", "geospatial", "viz", "viz.be_hillshade.tif"))
# plot(sedg_hillshade2)
# 
# sedg_hillshade2

# sedg_hillshade3 <- raster(here("data", "geospatial", "viz", "viz.hh_hillshade.tif"))
# plot(sedg_hillshade3)
# 
# sedg_hillshade4 <- raster(here("data", "geospatial", "viz", "viz.hh_hillshade-color.tif"))
# plot(sedg_hillshade4)

# contours_shp  <- read_sf(here("data", "geospatial", "contour", "contourfile.shp")) %>% 
#   st_transform(crs = 4326)
# contours_shx  <- st_read(here("data", "geospatial", "contour", "contourfile.shx")) %>% 
#   st_transform(crs = 4326)
# 
# contours_shp

# sedg_output_be <- raster(here("data", "geospatial", "rasters_CA20Brande", "output_be.tif"))
# plot(sedg_output_be)
# 
# sedg_output_hh <- raster(here("data", "geospatial", "rasters_CA20Brande", "output_hh.tif"))
# plot(sedg_output_hh)
# 
# sedg_output_srtm <- raster(here("data", "geospatial", "output_SRTMGL1.tif"))
# plot(sedg_output_srtm)
# 
# sedg_output_chm <- raster(here("data", "geospatial", "CHM", "output.dtm.tif"))
# plot(sedg_output_chm)
```

#Our trees: 
```{r}
#### Lee's version which hopefully cuts down on replicate values
wp_ind_long <- wp_ad %>%  #from data processing
  group_by(tree, site, plot, species, week, date, time) %>% 
  summarise(sd.mpa = sd(mpa), mpa = mean(mpa)) %>% 
  mutate(tree = as.character(tree))

# rename midday and predawn columns so I can combine them
wp_ind_md <- wp_ind_long[wp_ind_long$time=="md",]
wp_ind_md <- wp_ind_md %>% rename(md_mpa = mpa, date_md=date, md_sd.mpa = sd.mpa)

wp_ind_pd <- wp_ind_long[wp_ind_long$time=="pd",]
wp_ind_pd <- wp_ind_pd %>% rename(pd_mpa = mpa, date_pd=date, pd_sd.mpa = sd.mpa)

wp_ind <- full_join(wp_ind_md %>% select(-time), wp_ind_pd %>% select(-time))
wp_ind <- left_join(wp_ind, latlon, by=c("tree"))


# calculate delta Psi
wp_ind$e_drop <- wp_ind$md_mpa-wp_ind$pd_mpa

# add in lat lon and utm
wp_ind$lat_utm <- latlon.utm@coords[match( wp_ind$tree,latlon.utm$tree),2]
wp_ind$lon_utm <- latlon.utm@coords[match( wp_ind$tree,latlon.utm$tree),1]

#remove non-trees: 
wp_ind_new <- wp_ind %>% 
  drop_na(latitude, longitude) %>% 
  mutate(time = case_when(
    week < 17 ~ "early", 
    week > 18 ~ "late"
  ))

write_csv(wp_ind_new, here("processed-data", "geospatial", "wp_ind_new.csv"))
```

```{r}
#### Lee's version which hopefully cuts down on replicate values
wp_ind_long <- wp_ad %>%  #from data processing
  group_by(tree, site, plot, species, week, date, time) %>% 
  summarise(sd.mpa = sd(mpa), mpa = mean(mpa)) %>% 
  mutate(tree = as.character(tree))

# rename midday and predawn columns so I can combine them
wp_ind_md <- wp_ind_long[wp_ind_long$time=="md",]
wp_ind_md <- wp_ind_md %>% rename(md_mpa = mpa, date_md=date, md_sd.mpa = sd.mpa)

wp_ind_pd <- wp_ind_long[wp_ind_long$time=="pd",]
wp_ind_pd <- wp_ind_pd %>% rename(pd_mpa = mpa, date_pd=date, pd_sd.mpa = sd.mpa)

wp_ind <- full_join(wp_ind_md %>% select(-time), wp_ind_pd %>% select(-time))
wp_ind <- left_join(wp_ind, latlon, by=c("tree"))


# calculate delta Psi
wp_ind$e_drop <- wp_ind$md_mpa-wp_ind$pd_mpa

# add in lat lon and utm
wp_ind$lat_utm <- latlon.utm@coords[match( wp_ind$tree,latlon.utm$tree),2]
wp_ind$lon_utm <- latlon.utm@coords[match( wp_ind$tree,latlon.utm$tree),1]

#remove non-trees: 
wp_ind_new <- wp_ind %>% 
  drop_na(latitude, longitude) %>% 
  mutate(time = case_when(
    week < 17 ~ "early", 
    week > 18 ~ "late"
  ))

write_csv(wp_ind_new, here("processed-data", "geospatial", "wp_ind_new.csv"))
```

```{r}
wp_wc_ad <- read_csv(here("processed-data", paste0("wp_wc_rwc_",datver,".csv")), show_col_types = FALSE) 

#### Lee's version which hopefully cuts down on replicate values
wp_wc_ind_long <- wp_wc_ad %>%  #from data processing
  group_by(tree, site, plot, species, week, time) %>% 
  summarise(#sd.mpa = sd(mpa_mean, na.rm = T), 
            mpa = mean(mpa_mean, na.rm = T), 
            lwc = mean(lwc_mean, na.rm = T), 
            #sd.lwc = sd(lwc_mean, na.rm = T
                        ) %>% 
  mutate(tree = as.character(tree)) %>% 
  distinct()

## rename midday and predawn columns so I can combine them
wp_wc_ind_md <- wp_wc_ind_long[wp_wc_ind_long$time=="md",]
wp_wc_ind_md <- wp_wc_ind_md %>% rename(md_mpa = mpa, 
                                 # date_md=date, 
                                  md_lwc= lwc
                                 )

wp_wc_ind_pd <- wp_wc_ind_long[wp_wc_ind_long$time=="pd",]
wp_wc_ind_pd <- wp_wc_ind_pd %>% rename(pd_mpa = mpa, 
                                        #date_pd=date, 
                                        pd_lwc = lwc)

wp_wc_ind <- full_join(wp_wc_ind_md %>% select(-time), wp_wc_ind_pd %>% select(-time))
wp_wc_ind <- left_join(wp_wc_ind, latlon, by=c("tree"))


# calculate delta Psi
wp_wc_ind$e_drop <- wp_wc_ind$md_mpa-wp_ind$pd_mpa

# add in lat lon and utm
wp_wc_ind$lat_utm <- latlon.utm@coords[match( wp_wc_ind$tree,latlon.utm$tree),2]
wp_wc_ind$lon_utm <- latlon.utm@coords[match( wp_wc_ind$tree,latlon.utm$tree),1]

#remove non-trees: 
wp_wc_ind_new <- wp_wc_ind %>% 
  drop_na(latitude, longitude) %>% 
  mutate(time = case_when(
    week < 17 ~ "early", 
    week > 18 ~ "late"
  ))

write_csv(wp_wc_ind_new, here("processed-data", "geospatial", "wp_wc_ind_new.csv"))
```



```{r}
#With no water pots.
#trees <- read_csv(here("processed-data", "geospatial", "trees_latlon.csv"), show_col_types = F) 

#With water pots:
trees <- read_csv(here("processed-data", "geospatial", "wp_wc_ind_new.csv"), show_col_types = F)

# make a latlon and utm spatial data version
latlon.ll <- SpatialPointsDataFrame(coords = data.frame(trees$longitude, trees$latitude),
                                    proj4string = CRS("+proj=longlat +datum=WGS84"), 
                                    data=trees)
#make into the right projection: 
#latlon.utm <- spTransform(latlon.ll, CRSobj = crs(sedg_hillshade2))
```

#MPa

####Early in season (first month)
```{r}
wk10_mds <- latlon.ll@data  %>% 
  filter(week %in% c(10,11,12, 14)) %>% 
  group_by(tree) %>% 
  mutate(md_mpa = mean(md_mpa, na.rm = T)) %>% 
  arrange(desc(md_mpa)) %>% 
  drop_na(md_mpa)

pal_md <- colorNumeric(c( "#122451",
                                   "#004f63",
                                  "#62929a",
                                   "#859b6c",
                                  "#ffbb44",
                                  "#eb7926"
                                  ), domain = c(c(0,5.5)))

early_mds <- leaflet(wk10_mds) %>% 
  addTiles()  %>% 
  # addPolygons(data=contours_shx, color = grey) %>% 
  addCircleMarkers( radius = 5,
    color = ~ pal_md(md_mpa),
    stroke = FALSE, fillOpacity = 0.5) %>% 
   addProviderTiles("Esri.WorldTopoMap") %>% 
  addLegend("bottomright", pal = pal_md, values = ~md_mpa,
    title = "MPa",
    labFormat = labelFormat(prefix = "-"),
    opacity = 1
  )
early_mds
```

####End of season (mean of last month)

```{r}
wk33_mds <- latlon.ll@data  %>% 
  filter(week %in% c(29,33)) %>% 
  group_by(tree) %>% 
  mutate(md_mpa = mean(md_mpa, na.rm = T)) %>% 
  arrange(desc(md_mpa)) %>% 
  drop_na(md_mpa)

pal_md <- colorNumeric(c( "#122451",
                                   "#004f63",
                                  "#62929a",
                                   "#859b6c",
                                  "#ffbb44",
                                  "#eb7926"
                                  ), domain = c(c(0,5.5)))

late_mds <- leaflet(wk33_mds) %>% 
  addTiles() %>% 
  addCircleMarkers( radius = 5,
    color = ~ pal_md(md_mpa),
    stroke = FALSE, fillOpacity = 0.5) %>% 
   addProviderTiles("Esri.WorldTopoMap") %>% 
  addLegend("bottomright", pal = pal_md, values = ~md_mpa,
    title = "MPa",
    labFormat = labelFormat(prefix = "-"),
    opacity = 1
  )
late_mds
```

####Both maps together:

```{r}
sync_mpa <- leafsync::latticeView(early_mds, late_mds, ncol = 2, sync = list(c(1, 2)), 
                     sync.cursor = FALSE, no.initial.sync = FALSE)
sync_mpa

# mapview::mapshot(sync_mpa, file = here("figures", "sync_mpa.png"),
#           remove_controls = c("homeButton", "layersControl"))

save_tags(sync_mpa, here("figures", "sync_mpa.html"), selfcontained=TRUE)

#htmlwidgets::saveWidget(sync_mpa, file = here("figures", "sync_mpa.png"))
```

####Change over time: 

```{r}
chnge_wk10_to_wk33 <- latlon.ll@data%>% 
  filter(week %in% c(10, 33)) %>% 
  group_by(week, tree) %>% 
  summarise(md_mpa = mean(md_mpa), 
            pd_mpa = mean(pd_mpa)) %>% 
  pivot_wider(names_from = week, 
              values_from = c(pd_mpa, md_mpa)) %>% 
  mutate(change_mpa_md = md_mpa_33 - md_mpa_10, 
         change_mpa_pd = pd_mpa_33 - pd_mpa_10)

chnge_early_to_late <- latlon.ll@data%>% 
  #filter(week %in% c(10, 33)) %>% 
  group_by(time, tree, latitude, longitude) %>% 
  summarise(md_mpa = mean(md_mpa, na.rm = T), 
            pd_mpa = mean(pd_mpa, na.rm = T)) %>% 
  pivot_wider(names_from = time, 
              values_from = c(pd_mpa, md_mpa)) %>% 
  mutate(change_mpa_md = md_mpa_late - md_mpa_early, 
         change_mpa_pd = pd_mpa_late - pd_mpa_early) %>% 
  drop_na(change_mpa_md, change_mpa_pd)


chnge_early_to_late <- SpatialPointsDataFrame(coords = data.frame(chnge_early_to_late$longitude, chnge_early_to_late$latitude),
                                    proj4string = CRS("+proj=longlat +datum=WGS84"), 
                                    data=chnge_early_to_late)

pal <- colorNumeric(c("#eb7926", "#ffbb44", "#859b6c", "#62929a", "#004f63", "#122451"), domain = c(c(0,2)))

map_change <- leaflet(chnge_early_to_late) %>% 
  addTiles() %>% 
  addCircleMarkers( radius = ~ change_mpa_md * 5,
    color = ~ pal(change_mpa_md),
    stroke = FALSE, fillOpacity = 0.5) %>% 
   addProviderTiles("Esri.WorldTopoMap")%>% 
  addLegend("bottomright", pal = pal, values = ~change_mpa_md,
    title = "Change in MPa",
    labFormat = labelFormat(prefix = " "),
    opacity = 1
  )
map_change

mapview::mapshot(map_change, file = here("figures", "change_over_time.png"),
          remove_controls = c("homeButton", "layersControl"))
```

#LWC

Early in season (first month)
```{r}
wk10_mds <- latlon.ll@data  %>% 
  filter(week %in% c(10,11,12, 14)) %>% 
  group_by(tree) %>% 
  mutate(md_lwc = mean(md_lwc, na.rm = T)) %>% 
  arrange(desc(md_lwc)) %>% 
  drop_na(md_lwc)

pal_lwc <- colorNumeric(c( "#ce4441", "#ee8577","#eb7926", "#ffbb44", "#859b6c", "#62929a", "#004f63", "#122451"
                              
                                  ), domain = c(c(.4,2)))

early_lwc <- leaflet(wk10_mds) %>% 
  addTiles() %>% 
  addCircleMarkers( radius = 5,
    color = ~ pal_lwc(md_lwc),
    stroke = FALSE, fillOpacity = 0.5) %>% 
   addProviderTiles("Esri.WorldTopoMap") %>% 
  addLegend("bottomright", pal = pal_lwc, values = ~md_lwc,
    title = "lwc",
    labFormat = labelFormat(prefix = " "),
    opacity = 1
  )
early_lwc
```

End of season (mean of last month)

```{r}
wk33_lwc <- latlon.ll@data  %>% 
  filter(week %in% c(29,33)) %>% 
  group_by(tree) %>% 
  mutate(md_lwc = mean(md_lwc, na.rm = T)) %>% 
  arrange(desc(md_lwc)) %>% 
  drop_na(md_lwc)

pal_lwc <- colorNumeric(c( "#ce4441", "#ee8577", "#eb7926", "#ffbb44", "#859b6c", "#62929a", "#004f63", "#122451"
                                  ), domain = c(c(.4,2)))

late_lwc <- leaflet(wk33_lwc) %>% 
  addTiles() %>% 
  addCircleMarkers( radius = 5,
    color = ~ pal_lwc(md_lwc),
    stroke = FALSE, fillOpacity = 0.5) %>% 
   addProviderTiles("Esri.WorldTopoMap") %>%
  addLegend("bottomright", pal = pal_lwc, values = ~md_lwc,
    title = "lwc",
    labFormat = labelFormat(prefix = " "),
    opacity = 1
  )
late_lwc
```

View both maps together:

```{r}
lwc_synced <- leafsync::latticeView(early_lwc, late_lwc, ncol = 2, sync = list(c(1, 2)), 
                     sync.cursor = T, no.initial.sync = FALSE)
```

#ALL

```{r}
all_synced <- leafsync::latticeView(early_lwc, late_lwc, 
                                    early_mds, late_mds,
                                    ncol = 2, sync = list(c(1, 2,3,4)), 
                     sync.cursor = T, no.initial.sync = FALSE)
all_synced

save_tags(all_synced, here("figures", "all_synced.html"))
```



