---
title: "Combining WC, WP, LFM, and RWC data into one datasheet"
author: "Indra Boving"
date: "6/3/2022"
output: html_document
---

##setup


```{r setup, include=FALSE}
#install.packages("rstatix")
#devtools::install_github("an-bui/calecopal")

library(data.table)
library(janitor)
library(here)
library(tidyverse)
library(lubridate)
library(readxl)
library(gridExtra)
library(calecopal)
library(rstatix)

select = dplyr::select
 
#source("http://goo.gl/UUyEzD") #outlier KD (original function)
```

```{r}
## Data file version (so it's not hard coded in every read_excel() call)
datver <- "08182022"
dataversion <- paste0("Data_", datver)

tlp_qudo <- -2 #these are totally based on eyeballing Kelly's figure
tlp_quag <- -3
```

#---------------
#Rerun processing:
Run all scripts for processing to make sure those are updated: 

(NOTE: if changing datver, will have to change in each of these scripts)

```{r, warning=FALSE, eval=FALSE}
list.files("processing-scripts", full.names = TRUE) %>% walk(source)
```
#Combine DFs: 

#####WC:

Water content data looks like this: 

md_bulk_wet = as.numeric(md_bulk_wet), 
lwc_md_bulk = ((md_bulk_wet-md_bulk_dry)/md_bulk_dry)
lwc_pd_bulk = ((pd_bulk_wet - pd_bulk_dry)/pd_bulk_dry)
lwc_md_leaf = ((ww_g_md - dw_g_md)/dw_g_md)
lwc_pd_leaf = ((ww_g_pd - dw_g_pd)/dw_g_pd)) 

```{r}
wc_df <- read_csv(here("processed-data", paste0("wc_alldates_",datver,".csv"))) %>% #contains LWC data
  mutate(date = lubridate::ymd(date))%>% 
  select(-...1) %>% 
  mutate(timing = case_when(
    week %in% c(9, 10, 11, 12, 13, 14) ~ "early", 
    week %in% c(15, 16, 17, 18, 19, 20, 21, 29, 33) ~ "late"
  ))%>% 
  mutate(date_wc = date) %>% 
  #select(-date) %>% 
  #drop_na(date_wc)  %>% 
  drop_na(mpa)  %>% 
  mutate(time  = case_when(
     time %in% c("PD") ~ "pd", 
     time %in% c("MD") ~ "md", 
     TRUE ~"NA"
   ), 
   tree = case_when(
     tree == 2127 ~ 2327, #weird tree
     TRUE ~ tree
   ), 
   lwc_leaf = case_when(
     lwc_leaf >= 5 ~ NA_real_, #weird value
     TRUE ~ lwc_leaf
   )) %>% 
  select(-date, -mpa)

#WP:

wp_df <- read_csv(here("processed-data", paste0("wp_alldates_long_",datver,".csv"))) %>%
  #mutate(date = lubridate::ymd(date)) %>% 
  select(-...1, -rep) %>% 
  mutate(timing = case_when(
    week %in% c(9, 10, 11, 12, 13, 14) ~ "early", 
    week %in% c(15, 16, 17, 18, 19, 20, 21, 29, 33) ~ "late"
  )) %>%  
  mutate(tree = as.numeric(tree), 
         tree = case_when(
     tree == 2127 ~ 2327, #weird tree
     TRUE ~ tree), 
  date_wp = date) %>% 
  select(-tag, -plot_number, -date )

#WC + WP:

wp_wc_df <- merge(wp_df, wc_df, 
                  by = c("tree","plot", "site", "species", "time", "week"), 
                  all = T) %>% 
  filter(species != "ARCA", 
         species != "LEU") %>% 
  rowwise() %>% 
    mutate(lwc_mean = mean(c(lwc_bulk, lwc_leaf), na.rm = T), 
           timing = timing.x) %>% 
  dplyr::select(-timing.x, -timing.y)
  

wp_tmp <- wp_wc_df %>% 
  dplyr::select(tree, plot, site, species, time, mpa, date_wp, date_wc, week)

#tree info

trees_sites_df <- wp_wc_df %>% 
  select(tree, plot, site, species) %>% 
  distinct()
```

- some lwcs are missing! look into this (see google doc)

Need to find lwcs:

- week 19 (2022-05-09)
- week 9 (2022 - 02-28),
    -  specifically: tree 2085, 2086, 2087, 2088, 2090, 2348, 2349, 2361
- week 12 (2022-03-25), middays all
- week 15 (2022-04-13), trees: 2369, 2377
- week 17, tree 2383 MD,
- week 18, (2022-04-05), tree 2343 pd, 2346 pd, 2347 pd,  2365 pd, 2367 pd, 2369 pd, (all pds?)
- week 19 (2022-05-09) all?
- week 21 (20022-05-23) tree 2025 md, tree 2027 md, 2354 md
- week 29 (2022-07-19) tree 2020 pd, 2030 pd, 2376 pd, 2379 pd, 
- week 33 (2022 - 08-18) all (still need to be entered?)

#####RWC:

```{r}
rwc_df <- read.csv(here("processed-data", paste0("rwc_alldates_",datver,".csv")))

rwc_df %>% 
  #filter(week == 21) %>% 
  outlierKD(swc_per_dry_g)

rwc_df %>% 
  #filter(week == 21) %>% 
  outlierKD(swc_ww_g)

rwc_df %>% 
  #filter(week == 21) %>% 
  outlierKD(swc_dw_g)
```


```{r}
rwc_df_leaves_y0 <- rwc_df %>% 
  filter(type == "leaf", 
         year %in% c(0, "NA")) %>% 
  group_by(tree, date) %>% 
  mutate(mean_swc_per_dry_g = mean(swc_per_dry_g)
         , mean_swc_g = mean(swc_g)) %>% 
  ungroup() %>% 
  mutate(date_rwc = date, 
         week = as.numeric(week)) %>% 
  select(-date) %>% 
  distinct() %>% 
  select(mean_swc_per_dry_g, mean_swc_g, tree, week, date_rwc) %>% 
  as.data.frame()

rwc_df_leaves_y1 <- rwc_df %>% 
  filter(type == "leaf", 
         year %in% c(1, "NA")) %>% 
  group_by(tree, date) %>% 
mutate(mean_swc_per_dry_g = mean(swc_per_dry_g)
         , mean_swc_g = mean(swc_g)) %>% 
  ungroup() %>% 
  mutate(date_rwc = date, 
         week = as.numeric(week)) %>% 
  select(-date) %>% 
  distinct() %>% 
  select(mean_swc_per_dry_g, mean_swc_g, tree, week, date_rwc) %>% 
  as.data.frame()


#RWC + WC + WP:

wp_wc_rwc_df <- merge(wp_wc_df, rwc_df_leaves_y0 ,
                    by = c("tree",
                           "week"
                          # "rep"
                           ),
                    #all.x = T,
                    all.x = T
                    )

 # wp_wc_rwc_summary_df <- wp_wc_rwc_df %>% 
 #   group_by(week, tree) %>% 
 #   summarise(mean_md = mean(mpa_md), 
 #             mean_pd = mean(mpa_pd), 
 #             mean_lwc_md_bulk = mean(lwc_md_bulk), 
 #             mean_lwc_pd_bulk = mean(lwc_pd_bulk), 
 #             mean_swc_g = mean(mean_swc_g), 
 #             mean_swc_per_dry_g = mean(mean_swc_per_dry_g))
```

Something is up with week 21 (05/25/2022)

```{r}
rwc_df %>% 
  filter(year %in% c(0,1), 
         swc_per_dry_g < 5, 
         swc_percent < 300) %>% 
  ggplot(aes(y = swc_per_dry_g, 
             x = as.factor(week), 
             color = as.factor(type))) +
  geom_boxplot() +
  facet_wrap(~year) +
  labs(x = "Week", 
       y = "SWC (g water/g dry)", 
       color = "Type") +
  color
```

#####LFM:

Here we are splitting the LFM into different categories: stem vs. leaves, and y1 vs. y0. 

```{r}
lfm_leaves_y0_df <- read.csv( here("processed-data", paste0("lfm_alldates_",datver,".csv"))) %>% 
  filter(type == "leaf", 
         year == 0) %>% 
 mutate(lfm_wet_wt_y0_g = lfm_wet_wt_g, 
         lfm_wet_per_dry_y0_g = lfm_wet_per_dry_g, 
         lfm_dry_wt_y0_g = lfm_dry_wt_g, 
         lfm_y0_percent = lfm_percent, 
         tree = as.numeric(tree)) %>% 
  select(-year, -lfm_wet_wt_g, -lfm_dry_wt_g, -lfm_percent, -lfm_wet_per_dry_g, -X)


lfm_leaves_y1_df <- read.csv( here("processed-data", paste0("lfm_alldates_",datver,".csv"))) %>% 
  filter(type == "leaf", 
         year == 1) %>% 
  mutate(lfm_wet_wt_y1_g = lfm_wet_wt_g, 
         lfm_wet_per_dry_y1_g = lfm_wet_per_dry_g, 
         lfm_dry_wt_y1_g = lfm_dry_wt_g, 
         lfm_y1_percent = lfm_percent, 
         tree = as.numeric(tree)) %>% 
  select(-year, -lfm_wet_wt_g, -lfm_dry_wt_g, -lfm_percent, -lfm_wet_per_dry_g, -X)

lfm_stem_y0_df <- read.csv( here("processed-data", paste0("lfm_alldates_",datver,".csv"))) %>% 
  filter(type == "stem", 
         year == 0)

lfm_stem_y1_df <- read.csv( here("processed-data", paste0("lfm_alldates_",datver,".csv"))) %>% 
  filter(type == "leaf",
         year == 1)


lfm_both_both_df <- read.csv( here("processed-data", paste0("lfm_alldates_",datver,".csv"))) %>% 
  filter(type == "both",
         year == 3)  %>% 
  mutate(lfm_wet_wt_both_g = lfm_wet_wt_g, 
         lfm_wet_per_dry_both_g = lfm_wet_per_dry_g, 
         lfm_dry_wt_both_g = lfm_dry_wt_g, 
         lfm_both_percent = lfm_percent, 
         tree = as.numeric(tree), 
         date_lfm_both = date_lfm) %>% 
  select(-year, -lfm_wet_wt_g, -lfm_dry_wt_g, -lfm_percent, -lfm_wet_per_dry_g, -X)

lfm_leaves_df <- merge(lfm_leaves_y0_df, lfm_leaves_y1_df, 
                       by = c("tree", "time", "date_lfm", "week", "type"), all = T) %>% 
  distinct() 

lfm_leaves_both_df <- merge(lfm_leaves_df, lfm_both_both_df,
                            by = c("tree", "time", "date_lfm", "week", "type"), all = T) %>% 
  distinct() 
```

#####LFM + RWC + WC + WP (wide):

######RWC calc.

(percent lwc of saturated wc):

```{r}
wp_wc_rwc_lfm_df_wide <- merge(wp_wc_rwc_df, lfm_leaves_both_df, 
                               by = c("tree", "week", "time"), 
                               all = T) %>% 
  distinct() %>% 
  select(-site, -species, -plot)

wp_wc_rwc_lfm_df_wide_trees <- merge(trees_sites_df, wp_wc_rwc_lfm_df_wide, 
                                     by = c("tree")) %>% 
  select(-rep) %>% 
  distinct()

 #make a shorter name because the long one will be a pain to write out!
all_water_df <- wp_wc_rwc_lfm_df_wide_trees %>% 
  mutate(rwc_percent = ((lwc_mean/mean_swc_per_dry_g)*100))  #calculating RWC

write.csv(all_water_df, here("processed-data", paste0("LWC_LFM_WP_dates",datver,".csv")))
  
```

NOTE: This just includes leaves, need to make another df or add stems eventually.


######Missings: 

Q: What are we missing??? 

A: A lot....but where??

(This is each date we collected the associated metric, so if NA in that cell then we don't have it)

```{r}
missings_df <- wp_wc_rwc_lfm_df_wide_trees %>% 
  select(tree, week, species, site, plot, time, date_wp, date_wc, date_lfm, date_rwc) %>% 
  distinct()

write.csv(missings_df, here("processed-data", paste0("missing_LWC_LFM_WP_dates",datver,".csv")))
```

#####Outliers: 

10/26 - started this but need to confirm how we actually want to deal with outliers before moving ahead.

```{r}
outs_lwc <- all_water_df %>% 
  group_by(species, week) %>% 
  identify_outliers(lwc_leaf)

outs_lwc_mpa <- all_water_df %>% 
  group_by(species, week, time) %>% 
  identify_outliers(mpa)

outs_lfm <- all_water_df %>% 
  group_by(species, week, time) %>% 
  identify_outliers(lfm_y0_percent)

# without outliers: (something like this...)
# df %>% 
#   anti_join(outs, by = c("tree", "week")) %>% 
#   view()
```

#---------------
#Visualize!

####Water content dynamics: 

Bulk vs. individual leaf LWC...they should probably be the same? 

#####Leaf water content:

```{r}
all_water_df %>% 
  ggplot(aes(x = lwc_leaf,
             y = lwc_bulk, 
             color = species, 
             size = week)) +
  geom_jitter(alpha = .6) +
  geom_abline() +
  ylim(-1, 3) +
  xlim(0, 3) +
  color +
  facet_wrap(~species) +
  labs(caption = "black line is 1:1")
```


```{r}
all_water_df %>% 
    filter(lwc_mean < 4, 
         lwc_mean > 0,
         #lfm_percent > 20, 
  #        lfm_percent < 300) %>% 
  ) %>% 
  ggplot(aes(y = -1*mpa, 
             x = lwc_mean, 
             color = week 
             #size = week
             )) +
  geom_jitter(alpha = .6) +
  facet_wrap(~species)+
  labs(x = "LWC (g water/gram dry)", 
       y = "MPa", 
       color = "Week") +
  color_grad
```

```{r}
all_water_df %>% 
    filter(lwc_mean < 4, 
         lwc_mean > 0,
         #lfm_percent > 20, 
  #        lfm_percent < 300) %>% 
  ) %>% 
  ggplot(aes(x = -1*mpa, 
             y = lwc_mean, 
             color = week 
             #size = week
             )) +
  geom_jitter(alpha = .5) +
  facet_wrap(~species)+
  labs(y = "LWC (g water/gram dry)", 
       x = "MPa", 
       color = "Week") +
  color_grad
```
```{r}
all_water_df %>% 
    filter(lwc_mean < 4, 
         lwc_mean > 0,
         species == "blue oak"
         #lfm_percent > 20, 
  #        lfm_percent < 300) %>% 
  ) %>% 
  drop_na(site) %>% 
  ggplot(aes(x = -1*mpa, 
             y = lwc_mean, 
             color = week 
             #size = week
             )) +
  geom_jitter(alpha = .5) +
  facet_wrap(~site)+
  labs(y = "LWC (g water/gram dry)", 
       x = "MPa", 
       color = "Week", 
       title = "blue oak") +
  color_grad
```
```{r}
all_water_df %>% 
    filter(lwc_mean < 4, 
         lwc_mean > 0,
         species == "live oak"
         #lfm_percent > 20, 
  #        lfm_percent < 300) %>% 
  ) %>% 
  drop_na(site) %>% 
  ggplot(aes(x = -1*mpa, 
             y = lwc_mean, 
             color = week 
             #size = week
             )) +
  geom_jitter(alpha = .5) +
  facet_wrap(~site)+
  labs(y = "LWC (g water/gram dry)", 
       x = "MPa", 
       color = "Week", 
       title = "live oak") +
  color_grad
```

#####Relative water content: 

Reminder: RWC is combination of LWC and SWC, where:

SWC = g water/g dry after 2 hour rehydration (mean per tree/time of day/week)
LWC = g water/g dry (mean per tree/time of day/week)

RWC x LWC: 

```{r}
all_water_df %>% 
   filter(lwc_mean < 5,
          mean_swc_per_dry_g < 5) %>% 
  ggplot(aes(y = lwc_mean, 
             x = mean_swc_per_dry_g, 
             color = week 
             #size = week
             )) +
  geom_point(alpha = .6) +
  facet_wrap(~species)+
  labs(x = "Saturated Leaf Water Content", 
       y = "Field Leaf Water Content", 
       caption = "black line is 1:1") +
  color_grad +
  geom_abline()
```
```{r}
all_water_df %>% 
   filter(lwc_mean < 5,
          mean_swc_per_dry_g < 5) %>% 
  ggplot(aes(y = lwc_mean, 
             x = mean_swc_per_dry_g, 
             color = week 
             #size = week
             )) +
  geom_point(alpha = .6) +
  facet_wrap(~species)+
  labs(x = "Saturated Leaf Water Content", 
       y = "Field Leaf Water Content", 
       caption = "black line is 1:1") +
  color_grad +
  geom_abline()
```

RWC vs. MPa

```{r}
all_water_df %>% 
   filter(rwc_percent > 0, 
          rwc_percent < 300) %>% 
  ggplot(aes(y = -1*mpa, 
             x = rwc_percent, 
             color = as.factor(week)
             #size = week
             )) +
  geom_jitter() +
  facet_wrap(~species)+
  labs(x = "Relative Water Content", 
       y = "MPa") +
  color
```

```{r}
all_water_df %>% 
   filter(rwc_percent > 0, 
          rwc_percent < 300) %>% 
  ggplot(aes(y = -1*mpa, 
             x = rwc_percent, 
             color = interaction(species,time) 
             #size = week
             )) +
  geom_point(alpha = .6) +
  facet_wrap(~interaction(species, time))+
  labs(x = "Relative Water Content", 
       y = "MPa") +
  color
```
Q: What are the RWCs important for phsyiological thresholds? 

#####LFM: 

LFM x MPa, year 0

```{r}
all_water_df %>% 
  filter(lfm_y0_percent > 20, 
         lfm_y0_percent < 300) %>% 
  ggplot(aes(y = -1*mpa, 
             x = lfm_y0_percent, 
             color = week)) +
  geom_jitter(alpha = .6) +
  facet_wrap(~species) +
  color_grad +
  labs(y = "MPa", 
       x = "LFM, Y0")
```

LFM x MPa, year 1

```{r}
all_water_df %>% 
  filter(lfm_y1_percent > 20, 
         lfm_y1_percent < 300) %>% 
  ggplot(aes(y = -1*mpa, 
             x = lfm_y1_percent, 
             color = species)) +
  geom_point() +
  color +
  labs(y = "MPa", 
       x = "LFM, Y1")
```

LFM year 1 vs. year 0

```{r}
all_water_df %>% 
  filter(lfm_y1_percent > 20, 
         lfm_y1_percent < 300,
         lfm_y0_percent > 20, 
         lfm_y0_percent < 300)  %>% 
  ggplot(aes(y = lfm_y0_percent, 
             x = lfm_y1_percent, 
             color = species, 
             size = week)) +
  facet_wrap(~species) +
  geom_jitter(alpha = .6) + 
  geom_abline() +
  color
```



#---------------

#Ongoing issues: 


- water potentials for week 17 piney, cucu, and chamise are missing? (04.25.2022 and 04.27.2022) We have LFM and LWC for this week from those sites however.  

- missing LFM from week 18 (05.04.2022)













