---
.title: "introduction to sf and raster"
author: "Shane Dewees"
date: "2/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(sf)
library(raster)
library(leaflet)
```

## Loading in vector data and reprojecting it with sf package

```{r}
plots <- st_read(here("scripts", "other_peoples_code", "geospatial_examples","data", "sample_plots.shp")) %>% 
  st_transform(crs = 4326)

sb_county <- st_read(here("scripts", "other_peoples_code", "geospatial_examples","data", "sb_county.shp")) %>% 
  st_transform(crs = 4326)
```

## Basic graph to visualize data

```{r}
leaflet() %>% 
  addPolygons(data = sb_county) %>% 
  addMarkers(data = plots) %>% 
  addTiles()
```

## How to crop points to be within desired polygon

```{r}
plots_sb <- st_intersection(plots, sb_county) %>% 
  dplyr::select(Id, NAME) %>% 
  mutate(Id = 1:8) %>% 
  rename("county" = "NAME")


leaflet() %>% 
  addPolygons(data = sb_county) %>% 
  addMarkers(data = plots_sb) %>% 
  addTiles() %>% 
  addRasterImage(hillshade2, colors = pal, opacity = 0.8)

```

## We can add a buffer around our points to create new polygons

```{r}
plots_buffer <- st_buffer(plots, dist = 100)
leaflet() %>% 
  addPolygons(data = plots_buffer) %>% 
  addTiles()
```

## Now you try: 
- crop our plots_buffer layer to be only in Santa Barbara County
- make a new buffer layer with plots_sb 
- these should be identical. Graph them with leaflet and see if they overlap

```{r}

```


## Loading in and visualizing raster data

```{r}
sb_precip_normal <- raster(here("data", "sb_precip_normal.tif"))
sb_precip_normal
summary(sb_precip_normal)

plot(sb_precip_normal)

precip_normal_gg <- sb_precip_normal %>% 
  rasterToPoints() %>% 
  data.frame()

ggplot() +
  geom_sf(data = sb_county) +
  geom_raster(data = precip_normal_gg, aes(x= x, y = y, fill =sb_precip_normal))+
  geom_sf(data = plots_sb)

precip_normal_summary <- precip_normal_gg %>% 
  summarize(mean = mean(sb_precip_normal, na.rm = TRUE),
            median = median(sb_precip_normal, na.rm = TRUE),
            sd = sd(sb_precip_normal, na.rm = TRUE))

ggplot(precip_normal_gg) +
  geom_histogram(aes(x = sb_precip_normal))
```

## We can also crop raster data 

```{r}
sb_precip_normal_crop <- sb_precip_normal %>% 
  crop(plots_buffer) %>% 
  rasterToPoints() %>% 
  data.frame()

ggplot() +
  geom_sf(data = sb_county) +
  geom_raster(data = sb_precip_normal_crop, aes(x, y, fill = sb_precip_normal))+ 
  geom_sf(data = plots_buffer)
```

## We cab also resample raster pixel size, do raster math, and combine raster layers

```{r}
sb_precip_2003 <- raster(here("data", "sb_precip_2003.tif"))

sb_precip_normal_resample <- resample(x = sb_precip_normal, y = sb_precip_2003)

precip_2003_anomaly <- sb_precip_2003 - sb_precip_normal_resample 

plot(precip_2003_anomaly)

precip_brick <- brick(sb_precip_2003, 
                      sb_precip_normal_resample, 
                      precip_2003_anomaly)
plot(precip_brick)

precip_brick_math <- precip_brick - 1000

plot(precip_brick_math)

```

## Now you try:
 - Load in precip data for 2000 - 20002
 - Make a raster brick of those three layers
 - Caluclate precipitation anomaly for raster brick
 - plot it
 
```{r}

```
 

## Lastly, we can use sf and raster package together to extract raster data to points or polygons
```{r}
plots_sb_precip <- plots_sb %>% 
  mutate(precip_2003 = raster::extract(sb_precip_2003, plots_sb),
         precip_2003_anomaly = raster::extract(precip_2003_anomaly, plots_sb),
         precip_normal = raster::extract(sb_precip_normal_resample, plots_sb))

ggplot(plots_sb_precip, aes(x = precip_normal, y = precip_2003_anomaly)) +
  geom_point()
```

## Now you try: 
 -Extract 2000-2002 anomalies to plots_sb
 -graph a relationship with ggplot
 
```{r}

```
 
